---
title: "R Notebook"
output: html_notebook
---


```{r}
library(naniar)
library(hash)
library(assert)
library(ggplot2)
library(UpSetR)
```


```{r}
data = read.csv("Agrimonia_Dataset_v_3_0_0.csv")
head(data)
dim(data)
summary(data)
```

Dataset divided by station 
```{r}
df_stations=load("df_agri.Rdata")
dati = df_agri[,c(1,6)]
df_stat=hash()
stations = unique(dati$IDStations)
print(stations)

for (st in stations){
  df_stat[[st]] = dati[which(dati$IDStations == st),]
  assert(dim(df_stat[[st]])[1] == 2192) # make sure each df_stat has all his 2192 obs
}
```



Choose which stations to exclude and save them in a list 
We can change threshold 
Problem is some station lack only some measurements
  threshold = 2000 -> only remove stations with no pm_10 measurements
  threshold < 2000 -> based on our tolerance, may depend on year chosen 
```{r}
df_stat=hash()
stat_to_exclude=0
for (st in stations){
  df_stat[[st]] = dati[which(dati$IDStations == st),]
  
  #print(sapply(df_stat[[st]],function(x) sum(is.na(x))))
  
  if(sapply(df_stat[[st]],function(x) sum(is.na(x)))[2]>1000){
    stat_to_exclude=append(stat_to_exclude,st)
  }
}
stat_to_exclude=stat_to_exclude[-1]
print(stat_to_exclude)
```

Removing selected stations
```{r}
new_dataset=data[which(!(data$IDStations %in% stat_to_exclude)),]
```

Count of na for each column
```{r}
print(sapply(new_dataset,function(x) sum(is.na(x))))
```


Removing AQ_columns (too many na)
```{r}
new_dataset=subset(new_dataset,select=-c(AQ_pm25,AQ_co,AQ_nh3,AQ_nox,AQ_no2,AQ_so2,LA_soil_use))
```
Only remaining columns with less than 40000 nas

```{r}
print(sapply(new_dataset,function(x) sum(is.na(x))))
```

Still some nas given by columns and stations with partial masurements
Maybe better to remove them after selecting the year
Can use timeseries


Save the dataset
```{r}
write.csv(new_dataset,file="reduced_dataset.csv")
```




