---
title: "R Notebook"
output: html_document
---

```{r,warning = FALSE}
library(drpm)
library(salso)

# preparation
source("include.R") # for having df_agri
source("plot functions/plotter.R")

sites = data.frame(
	longitude = unique(df_weekly$Longitude), 
	latitude = unique(df_weekly$Latitude))
```

better to leave this alone (less buggy but dont know why).
```{r}
source("include_clusters_functions.R")
```


# create a pm10 table (station x time)
```{r}
stations = unique(df_wsc$IDStations)
y=data.frame()

for(st in stations){
  y_we_pm10=cbind(as.data.frame(st),t(df_wsc[which(df_wsc$IDStations==st),"AQ_pm10"]))
  y=rbind(y,y_we_pm10)
}

rownames(y) = NULL
colnames(y)<- c("id",paste0("w", 1:53))
df_wsc
y
```


# Trend plots

```{r}
yred=y[,2:54]
cols = colora(size(yred)[1],56,0)
for(i in 1:size(yred)[1]){
   if(i==1){
     plot(1:size(yred)[2],yred[i,],col=cols[i],ylim=extrema(yred),type='l',xlab='weeks',ylab='pm10')
 	  } 
	  else{
		  lines(1:size(yred)[2],yred[i,],col=cols[i])
	  }
}
```

```{r}
cols = colora(105,56,show=F)
chosen_variable_name = "AQ_pm10"

trendYearStation_week <- function(file_name){

	data_from_to = df_wsc
	len_time = 54
	
	chosen_variable = (data_from_to[,chosen_variable_name])

	# Crea il grafico ggplot
	station_trend <- ggplot(data_from_to,aes(x = week, 
												 y = AQ_pm10,
												 group=IDStations, 
												 color = as.factor(IDStations))) +
		
		geom_line(show.legend = FALSE) +
		labs(x = "Stations", y = chosen_variable_name, title = "Year: 2018 all stations") +
		ylim(range(na.omit(chosen_variable))) +
		scale_color_manual(values = cols) +
		theme_bw()+
		theme(panel.grid = element_blank()) +
		guides(color = guide_legend())+
		labs(x="week")
	
	len_time = (len_time%/%5)
	return(trend_animator(file_name,station_trend, data_from_to$week,len_time))
}
trendYearStation_week("None")
```



# Model fit

## Scaling/Centering update
```{r}
time_span = 1:10 # low time span for quick testing, real one will be 1:53

### authors suggested to/did scale the spatial locations and also centered the observations
y_fit = y[,1+time_span]
y_fit

### and for the scaling of spatial locations
std_sites = data.frame(
	longitude = unique(df_wsc$Longitude), 
	latitude = unique(df_wsc$Latitude))

plot(sites)
plot(std_sites)
```

## Fit
Burn in needs to be >= 10000. This after some long fits with low nburn (to see the whole behaviour of the MCMC) where there are some relevant changes even after 10000 iterations. So a lot of them needs to be discarded. I would set burn in to also 20000 maybe.

```{r}
niter=8000; nburn=4000; nthin=4
# niter=60000; nburn=20000; nthin=40 # original
# niter=100000; nburn=60000; nthin=40 # new one for more data
nout <- (niter-nburn)/nthin
cat(nout,"valid iterations\n")
```

```{r}
seed_choice = round(runif(1,0,1000))
set.seed(seed_choice)
cat(paste0("seed ",seed_choice,"\n==========================\n",date(),"\n\n"))
tempo_inizio <- Sys.time()
drpm1 <- drpm_fit(y=y_fit, 
		 s_coords = std_sites,
         M=1,
         initial_partition = NULL,
         starting_alpha = 0.5,
         unit_specific_alpha = FALSE,
         # time_specific_alpha = TRUE, # meaning a bit ambiguos
		# Ok after experimenting it means that:
		# - if true we let alpha be a param that changes over time. 
		#	At time 1 we have a chain with some behaviour, 
		#	at time 2 another chain with another behaviour, ecc
		# - if false we instead fix alpha, ie all chains of all times
		#	will be the same, as they refer to the same parameter estimation
		# The authors in their tests set it to false, ie the fixed alpha
         alpha_0=FALSE, # modello temporale, questa deve sempre essere falsa
		
		# parameters from the drpm models comparison:
		# case E0P1A1
         eta1_0=FALSE,
         phi1_0=TRUE,
         time_specific_alpha = TRUE,

         # modelPriors=c(0,100^2,1,1,1,1), # original default one
         modelPriors=c(0,100,10,5,5,2,2,1), # author suggestion/used one

		 # così con 1,1 è una uniforme
         alphaPriors=rbind(c(1,1)), # if time_specific_alpha == TRUE
         # alphaPriors=matrix(rep(c(1,1),105),105,2), # if unit_specific_alpha == TRUE
         # alphaPriors=matrix(rep(c(1,1),105),105,2), # if both the above are TRUE

         simpleModel = 0,
         theta_tau2 = c(0, 2), # only used if simpleModel=1

         # SpatialCohesion=3, # auxiliary similarity
         SpatialCohesion=4, # double dipper similarity, default one

         # cParms=c(0, 1, 2, 1), # default one
         cParms=c(0, 1, 5, 1), # author suggestion/used one (with 5)
		
         # mh=c(0.5,1,0.1, 0.1, 0.1), # default one
		 mh=c(0.1,0.1,0.7, 0.1, 0.1), # with a bit of author suggestion/used one

         verbose=TRUE,

         # draws=1100,burn=100,thin=1) # quick one
         # draws=31000,burn=1000,thin=1) # for trace plot analysis
         # draws=8000,burn=3000,thin=5) # a bit more serious seriou one
         # draws=10000,burn=2000,thin=8) # more serious one
         draws=niter,burn=nburn,thin=nthin) # adaptable one

tempo_fine <- Sys.time()
differenza_tempo <- tempo_fine - tempo_inizio
cat(crayon::cyan("Fit took:\n"))
print(round(differenza_tempo,digits = 4))

cat(crayon::blue("That was for fitting",max(time_span),"time steps.\nSo for fitting all 53 weeks the expected time with these parameters will be:\n"))
print(round(differenza_tempo/max(time_span)*53,digits=4))

cat(crayon::red("\nLPML =",drpm1$lpml, "\nWAIC =",drpm1$waic))
```


## model save
```{r}
model_name = "pm_test_for_tesi"
# model_name = "pm_eta0_phi1_spcoes5_v2"
save(drpm1,file=paste0("../data/Federico/",model_name,".Rdata"))
```

=============================
final result
=============================
_1)_ drpm_eta0_phi1_spcoes5
Lui è il migliore
seed 725
LPML = 3612.91277963648 
WAIC = -7982.83537806802

_2)_ drpm_eta0_phi1_spcoes5_v2
longer run, 100k iterazioni, 60k burn in
seed 509
LPML = 3504.75360390795 
WAIC = -8050.23259569603

--------------------------------------------

_1.1)_ drpm_eta0_phi1_spcoes5_run2
seed 641
LPML = 3485.84498476289 
WAIC = -7995.67709001916
run2 perchè maggiore burn in e minore thinning

_2)_ drpm_eta0_phi0_spcoes5
seed 124
LPML = 3486.79593082633 
WAIC = -7820.27001567447

_3)_ drpm_eta1_phi1_spcoes5
seed 32
LPML = 2504.73101147775 
WAIC = -5299.37076656157
pessimo, come confermato dal models comparison

_4)_ drpm_eta1_phi0_spcoes5
non vale farlo, era anche lui in basso nel model comparison

====================
old tests
====================
Fittig seriously, and on 30 weeks
LPML = 1860.18778637473 
WAIC = -4121.29141752817

Again on 30 weeks but quicker show less fitting goodness
LPML = 1370.56163617035 
WAIC = -3002.68219081088

Better (using 4 as dof in NIG)
ma il fit non era su tutte le settimane, era sulle prime 6
LPML = 304.537399598655 
WAIC = -702.001549273177

Worse (using 5 as dof in NIG)
ma il fit non era su tutte le settimane, era sulle prime 6
LPML = 285.202489478406 
WAIC = -646.215550051243

```{r}

drpm1$mu[,1:7,5]
```


```{r}
dim(drpm1$Si)
drpm1$Si[,,2]
```


```{r}
names(drpm1)
# size(drpm1$Si)
# questa cos ha le simulazioni dei cluster assegnati
# ha dimensione 53 righe (o meno se fittiamo su meno tempi per dei test),
# poi ha 105 colonne, e 1000 "volte", perché
# - per ognuna delle 1000 iterazioni delle MCMC
# - dà i cluster assegnati dalla simulazione per le stazioni in quella simulazione


# the row dimensione will be 53, for now is time_span limit (like 5)
cat("\nSi     size = ",size(drpm1$Si),"\n")
cat("gamma  size = ",size(drpm1$gamma),"\n")
cat("mu     size = ",size(drpm1$mu),"\n")
cat("sig2   size = ",size(drpm1$sig2),"\n")
cat("alpha  size = ",size(drpm1$alpha),"\n")
cat("theta  size = ",size(drpm1$theta),"\n")
cat("tau2   size = ",size(drpm1$tau2),"\n")
cat("eta1   size = ",size(drpm1$eta1),"\n")
cat("phi0   size = ",size(drpm1$phi0),"\n")
cat("phi1   size = ",size(drpm1$phi1),"\n")
cat("lam2   size = ",size(drpm1$lam2),"\n")
cat("llike  size = ",size(drpm1$llike),"\n")
cat("fitted size = ",size(drpm1$fitted),"\n")
```



## model load
```{r}
# model_name = "drpm_eta0_phi1_spcoes5"
# load(paste0("../data/Federico/",model_name,".Rdata"))
```


# Trace plots?
```{r}
sampled_station = floor(runif(1,1,105))
cat("sampled_station =",sampled_station,"- that is station called",unique(df_wsc$IDStations)[sampled_station])
sampled_station_name = unique(df_wsc$IDStations)[sampled_station]

time_span_plot = c(1:10)
```

## alpha
It depends:
- if time_specific_alpha = FALSE we get the same MCMC, ie the same plots
- if time_specific_alpha = TRUE we get different MCMC, alpha behaviour changes in time
- if unit_specific_alpha = ecc but we dont use this option
```{r}
dim(drpm1$alpha)
```
```{r}
if(len(size(drpm1$alpha))==2){ # alpha is not unit dependent
	for (time in time_span_plot){
	# cat("Week",time,"- alpha mean value =",mean(drpm1$alpha[,time]),"\n")
	plot(drpm1$alpha[,time],type="l",
		 main=bquote("Trace plot of " * alpha[.(time)] 
		 * " (mean value = " * .(mean(drpm1$alpha[,time])) * ")"
		 ),
		 xlab = "MCMC iterations",ylab="values")
	}
}

if(len(size(drpm1$alpha))==3){ # alpha is unit dependent 
	for (time in time_span_plot){
	plot(drpm1$alpha[time,sampled_station,],type="l",
		 main=bquote("Trace plot of " * alpha[.(time)] * " - station" * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
	}
}
```

## Si
There are MCMC with time and with stations.
```{r}
dim(drpm1$Si)
```
```{r}
for (time in time_span_plot){
	plot(drpm1$Si[time,sampled_station,],type="l",
		 main=bquote("Trace plot of partition "*rho* " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
```

## gamma
Gamma is not really a parameter but the collection of the alphas.
So we dont care abouth her trace plot.

## mu
Same as Si, there are MCMC with time and with stations.
```{r}
dim(drpm1$mu)
```
```{r}
for (time in time_span_plot){
	plot(drpm1$mu[time,sampled_station,],type="l",
		 main=bquote("Trace plot of " * mu * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span_plot){
	par(mar=c(4,4,3,2))
	acf(drpm1$mu[time,sampled_station,],main=bquote("ACF plot of " * mu * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)))
}
```

## sigma2
Same as mu and Si
```{r}
dim(drpm1$sig2)
```
```{r}
for (time in time_span_plot){
	plot(drpm1$sig2[time,sampled_station,],type="l",
		 main=bquote("Trace plot of "* sigma^2 * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span_plot){
	par(mar=c(4,4,3,2))
	acf(drpm1$sig2[time,sampled_station,],main=bquote("ACF plot of " * sigma^2 * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)))
}
```

## theta
MCMC for each time, one for all stations.
```{r}
dim(drpm1$theta)
```
```{r}
for (time in time_span_plot){
	plot(drpm1$theta[,time],type="l",
		 main=bquote("Trace plot of " * theta * " at week "*.(time)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span_plot){
	par(mar=c(4,4,3,2))
	acf(drpm1$theta[,time],main=bquote("ACF plot of " * theta * " at week "*.(time)))
}
```


## tau2
MCMC for each time, one for each station.
```{r}
dim(drpm1$tau2)
```
```{r}
for (time in time_span_plot){
	plot(drpm1$tau2[,time],type="l",
		 main=bquote("Trace plot of " * tau^2 * " at week "*.(time)),
		 xlab = "MCMC iterations",ylab="values")	
}
```

## eta1
MCMC for each station, no time involved
```{r}
dim(drpm1$eta1)
```
```{r}
plot(drpm1$eta1[,sampled_station],type="l",
	 main=bquote("Trace plot of " * eta[1] *" - station " * .(sampled_station_name)),
	 xlab = "MCMC iterations",ylab="values")	
```

## phi0
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$phi0)
```
```{r}
plot(drpm1$phi0[,1],type="l",
	 main=bquote("Trace plot of "* phi[0]),
	 xlab = "MCMC iterations",ylab="values")
```

## phi1
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$phi1)
```
```{r}
plot(drpm1$phi1[,1],type="l",
	 main=bquote("Trace plot of "* phi[1]),
	 xlab = "MCMC iterations",ylab="values")
```

## lambda2
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$lam2)
```
```{r}
plot(drpm1$lam2[,1],type="l",
	 main=bquote("Trace plot of "* lambda^2),
	 xlab = "MCMC iterations",ylab="values")
```


# Map cluster plots
come loss o usare la classica binder ma con maxnclusters limitato, o provare con VI
```{r}
# loss = binder(a=1) # plus maxNClusters = 6 or similar
loss = "VI"
# loss = "VI.lb" # generally not recomended, lo dicono gli autori di salso

# loss = "NVI"
# loss = "NID"
```


## dataframe for clusters
```{r,warning=FALSE}
df_cluster = data.frame(Longitude=c(),Latitude=c(),values=c(),clusters=c(),Time=c())
for(time in time_span){

	salso_out <- salso(t(drpm1$Si[time,,]),
					   loss=binder(a=1),
					   # loss="VI",
					   # loss="VI.lb",
					   maxNClusters = 6
					   )
	
	df_temp = data.frame(
		Longitude = sites$longitude,
		Latitude = sites$latitude,
		clusters = salso_out[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster = rbind(df_cluster,df_temp)
	
	
	
	# clusters log
	clusters_now = df_temp$clusters
	# n_clusters = max(clusters_now)
	n_clusters = unique(clusters_now)
	ycurrent = y[,paste0("w",time)]
	cat(crayon::red("Time",time,"- #clusters =",length(unique(clusters_now)),"\n"))
	# for (cl in n_clusters){
		# cat("Cluster",cl,"- size",length(ycurrent[which(clusters_now==cl)]),
			# "- mean",mean(ycurrent[which(clusters_now==cl)]),"\n")
	# }
}
```



## ARI plot
```{r,wanring=F}
library(mclust)
##########################
FIT = drpm1 # your fit
LEN = max(time_span)
##########################

# build the ARI matrix
ARImats <- matrix(NA, nrow=LEN, ncol=LEN)
rho_ARI <- list()
for(k in 1:LEN){
	rho_ARI[[k]] <- salso(t(FIT$Si[k,,]),
						  loss=binder(a=1),
						  # loss="VI",
						  # loss="VI.lb",
						  maxNClusters = 6
						  ) # adjust with your fit $Si dimension
}
for(k in 1: LEN){
	for(kk in 1: LEN){
		ARImats[k,kk] <- adjustedRandIndex(rho_ARI[[k]], rho_ARI[[kk]])
	}
}
hist(ARImats)
```

Negative ARI says that the agreement is less than what is expected from a random result. 
This means the results are 'orthogonal' or 'complementary' to some extend.


```{r,wanring=F}
# pdf(paste0("./figures/Federico/LaggedARI_",model_name,".pdf"), height=8, width=10)
ncols_ari = 100
if (min(ARImats)<0){
	cols_ARI = colora(ncols_ari,79,0)
	brks = seq(floor(min(ARImats)),1,length.out=ncols_ari+1)
} else {
	cols_ARI = colora(ncols_ari,56,0)
	cols_ARI = rev(cols_ARI) # must be ordered from cold to warm
	brks = seq(0,1,length.out=ncols_ari+1)
}
# or see ?designer.colors for colors
library(fields)
image.plot(ARImats,
		   main=paste0("Lagged ARI values - model ",model_name),axes=FALSE,col=cols_ARI,
		   breaks=brks)
mtext(text=c(paste("",1:LEN)), side=2, line=0.3,at=seq(0,1,length=LEN), las=1, cex=0.8)
mtext(text=c(paste("",1:LEN)), side=1, line=0.3,at=seq(0,1,length=LEN), las=2, cex=0.8)
# dev.off()
```


# Clusters distribution

## cols choice
now it's inside include clusters functions


## plot functions
```{r,warning=FALSE}
clusters_old = NULL
for(time in time_span[1:10]){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	# clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now

	# p = get_hist_continuos_plot(df_cluster_cut,verbose=0)
	# p = get_hist_color_plot(df_cluster_cut)
	# p = get_hist_fill_plot(df_cluster_cut)
	cols = color_correct_clusters(df_cluster_cut,idea=1,verbose=0)
	p = get_boxplot_plot(df_cluster_cut,cols)
	print(p)
	# plot_graph_and_hist(df_cluster_cut)
	
	clusters_old = clusters_now
} # end for(time in eccc)
```


# Fede: graph cluster plot

## Version 2 - final
all the functions are in the include_clusters_function. Here is the code to plot.
```{r}
# cols chosen previously
clusters_old = NULL
for(time in time_span){
	cat(crayon::red("Time",time,"\n"))
	
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now,very_verbose = 0)
	df_cluster_cut$clusters = clusters_now
	
	q = get_graph_plot(df_cluster_cut)
	
	print(q)
	clusters_old = clusters_now
}
```


## new heat plot
```{r}
clusters_old = NULL
for(time in time_span[1:10]){
	cat(crayon::red("Time",time,"\n"))
	
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	####### no mode correct now
	# clusters_now = mode_correct_clusters(clusters_old,clusters_now,very_verbose = 0)
	# se fai heat plot non serve fare la mode correct
	# perché la heat plot la usi per vedere anche i valori di pm10, non la coerenza temporale
	# nei gruppi, che con la heat coloration si perde come visibilità (non so se è chiaro)
	df_cluster_cut$clusters = clusters_now
	
	# meglio l'idea 1
	cols = color_correct_clusters(df_cluster_cut,idea=1,verbose=0)
	
	# q = get_graph_plot(df_cluster_cut,cols)
	# print(q)
	p = plot_graph_and_hist(df_cluster_cut,cols)
	
	clusters_old = clusters_now
	
}
```


# Gif creation

```{r}
percorso = "./figures/Federico/heat/"
###################################
# save images
###################################
clusters_old = NULL
for(time in time_span){
	cat(crayon::red("Time",time,"\n"))

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	# clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now

	cur_num = sprintf("%02d", time)
	cols = color_correct_clusters(df_cluster_cut,idea=1,verbose=0)
	
	q = get_graph_plot(df_cluster_cut,cols)
	print(q)
	ggsave(file=paste0(percorso,model_name,"-graph",cur_num,".png"),
		   units="px",width=2000, height=1400, dpi=300)
	
	# p = plot_graph_and_hist(df_cluster_cut,cols)
	# ggsave(file=paste0("./figures/Federico/",model_name,"-graph_boxplot",cur_num,".png"),plot=p,
		   # units="px",width=2500, height=1400, dpi=300)
	
	dev.off()


clusters_old = clusters_now
}


###################################
# build gif
###################################
# Carica i pacchetti
library(magick)
library(animation)
library(gifski)
library(av)

## list file names and read in
imgs <- list.files(path = percorso, pattern = ".png", full.names = TRUE)
img_list <- lapply(imgs, image_read)

## join the images together
img_joined <- image_join(img_list)

## animate at 1 frames per second. 1 to freely control the fps/framerate later
img_animated <- image_animate(img_joined, fps = 1)

## view animated image
# img_animated

## save to disk
# delay is the inverse of framerate
frammeratte = 2
image_write_gif(image = img_animated, path = paste0(percorso,model_name,".gif"),delay=1/frammeratte)
image_write_video(image = img_animated, path = paste0(percorso,model_name,".mp4"),framerate=frammeratte)
```



