---
title: "Untitled"
output: html_document
---

# Setup
```{r,warning = FALSE}
library(drpm)
library(salso)
library(grDevices) # for image saving

# preparation
source("include.R") # for having df_agri
source("plot functions/plotter.R")

sites = data.frame(
	longitude = unique(df_weekly$Longitude), 
	latitude = unique(df_weekly$Latitude))
```

better to leave this alone (less buggy but dont know why).
```{r}
source("include_clusters_functions.R")
```

create a pm10 table (station x time)
```{r}
stations = unique(df_wsc$IDStations)
y=data.frame()

for(st in stations){
  y_we_pm10=cbind(as.data.frame(st),t(df_wsc[which(df_wsc$IDStations==st),"AQ_pm10"]))
  y=rbind(y,y_we_pm10)
}

rownames(y) = NULL
colnames(y)<- c("id",paste0("w", 1:53))
df_wsc
y
```


```{r}
cols = colora(105,56,show=F)
chosen_variable_name = "AQ_pm10"

trendYearStation_week <- function(file_name){

	data_from_to = df_wsc
	len_time = 54
	
	chosen_variable = (data_from_to[,chosen_variable_name])

	# Crea il grafico ggplot
	station_trend <- ggplot(data_from_to,aes(x = week, 
												 y = AQ_pm10,
												 group=IDStations, 
												 color = as.factor(IDStations))) +
		
		geom_line(show.legend = FALSE) +
		labs(x = "Stations", y = chosen_variable_name, title = "Year: 2018 all stations") +
		ylim(range(na.omit(chosen_variable))) +
		scale_color_manual(values = cols) +
		theme_bw()+
		theme(panel.grid = element_blank()) +
		guides(color = guide_legend())+
		labs(x="week")
	
	len_time = (len_time%/%5)
	return(trend_animator(file_name,station_trend, data_from_to$week,len_time))
}
trendYearStation_week("None")
```

standardize space coordinates
well now we can get them from df_wsc
```{r}
std_sites = data.frame(
	longitude = unique(df_wsc$Longitude), 
	latitude = unique(df_wsc$Latitude))
std_sites
```


```{r}
plot(sites)
plot(std_sites,col="blue")
```


# Models fit
```{r}
time_span = 1:16 # low time span for quick testing, real one will be 1:53

### authors suggested to/did scale the spatial locations and also centered the observations
y_fit = y[,1+time_span]
tps = ncol(y_fit)
y_fit
### and for the scaling of spatial locations we already built
std_sites
```


```{r}
# modelPriors = c(m0, s20, Asig, Atau, Alam, a, b, be)
# m0 - mean of phi0, phi0 is the mean of theta, theta is the mean of Y
# s20 - variance of theta, ecc

# Asig - maximum value for sigma
#	[0,Asig] is the support of the uniform in which sigma (std dev of Y) varies
# Atau - maximum value for tau
#	[0,Asig] is the support of the uniform in which mu (mean of Y) varies
# Alam - maximum value for lambda
	# lambda is a unuform on [0,Alam]
	# lambda is the var of tau, tau is the var of sigma, sigma is the var of Y

# a - shape 1 for alpha
# b - shape 2 for alpha
# b - scale for eta1
modelPriors <- c(0,100, 10, 5, 5, 2, 2, 1)

# m, k0, nu0, L0
# cParms <- c(0,1,5,1)
cParms <- c(0,1,5,1) # as authors

# SIG, TAU, LAM, ETA1, PHI1
# mh <- c(1,1, 1, 0.1, 0.1)
mh <- c(0.1,0.1, 0.7, 0.1, 0.1) # i changed this for sigma2 trace plots
sp <- 4
```


```{r}
# niter=50000; nburn=10000; nthin=40 # real one
niter=30000; nburn=15000; nthin=15
nout <- (niter-nburn)/nthin
cat(nout,"valid iterations")
```


```{r}
set.seed(1)
models.out <- list()
hh <- 1
# h <- "111"; s <- "0";
model <- "AR1"

# for(s in c("0","1")){ # we want to use space
# authors did also space comparison as it was the paper topic also

models_vector = c("E1P1A1","E1P1A0","E1P0A1","E1P0A0","E0P1A1","E0P1A0","E0P0A1","E0P0A0")
for(h in models_vector){
	# readline(prompt="Press [enter] to continue fitting") # to let the pc breath
	cat(paste0("fitting model ",hh," (",models_vector[hh],")...\n"))

	m.n <- as.numeric(strsplit(h, "")[[1]][c(2,4,6)])
	
	eta1_bool <- m.n[1]!=0
	phi1_bool <- m.n[2]!=0
	alphat_bool <- m.n[3]!=0
	# we select true if the number in h was 1, ie "!=0"
	
	# we always want to use space
	# if(s=="0"){
		# sc <- NULL
	# } else {
		sc <- std_sites
	# }

	tempo_inizio <- Sys.time()
	set.seed(1*hh)
	sink(nullfile()) # suppress output
	out <- drpm_fit(draws=niter, burn=nburn, thin=nthin,
					y=y_fit, M=1, s_coords=sc,
					# global_alpha=FALSE, # forse intendevano questi due comandi dopo:
					unit_specific_alpha=FALSE,
					
					# maybe our tests should be concentrated here
					# ie testing with this TRUE or FALSE
					time_specific_alpha=alphat_bool, # meaning a bit ambiguos
					# Ok after experimenting it means that:
					# - if true we let alpha be a param that changes over time. 
					#	At time 1 we have a chain with some behaviour, 
					#	at time 2 another chain with another behaviour, ecc
					# - if false we instead fix alpha, ie all chains of all times
					#	will be the same, as they refer to the same parameter estimation
					# The authors in their tests set it to false, ie the fixed alpha
  				
  					modelPriors=modelPriors,
					# ... as testing on this alpha_0 does not seem really relevant
					# i mean alpha should always be let able to change
					# if we set alpha_0 = TRUE we would never update alpha, but that's not our
					# interest (it was in the interest of the paper marketing)
  					alpha_0 = FALSE,
  					eta1_0 = eta1_bool,
  					phi1_0 = phi1_bool,
  					SpatialCohesion=sp, cParms=cParms,mh=mh,
					verbose=FALSE)
	sink() # end suppress output
	
	tempo_fine <- Sys.time()
	cat(crayon::red("##############################\n"))
	cat(crayon::cyan("Model is",paste0(h),"ie:"),
		"\neta1_bool =",eta1_bool,"-",
		"phi1_bool =",phi1_bool,"-",
		"alphat_bool =",alphat_bool,"-",
		"\n")
	# cat("seed is", 1*hh, "\n")
	cat("\n")
	differenza_tempo <- tempo_fine - tempo_inizio
	cat("Fit took:\n")
	print(round(differenza_tempo,digits = 4))

	# print(date())
	cat(h,"lpml = ", out$lpml, "\n")
	cat(h,"waic = ", out$waic, "\n")
	cat(crayon::red("##############################\n"))
	models.out[[hh]] <- out
	names(models.out)[hh] <- paste0("out_",h,"_",model)

	# rho <- list()
	# for(k in 1:tps){
	# 	# rho[[k]] <- salso(t(out$Si[k,,]), loss="VI")
	# 	rho[[k]] <- salso(t(out$Si[k,,]), loss="binder")
	# }

	hh <- hh + 1
}
# }
```


```{r}
save(models.out,file="../data/Federico/drpm_comparison.Rdata")
```

# Trace plots
to check if all models reach convergence in the MCMC iterations.

```{r}
sampled_station = floor(runif(1,1,105))
cat("sampled_station =",sampled_station,"- that is station called",unique(df_wsc$IDStations)[sampled_station])
sampled_station_name = unique(df_wsc$IDStations)[sampled_station]
```

```{r}
for (hh in 1:length(models_vector)){
	modcur = models.out[[hh]]
	cat(names(models.out)[[hh]],"\n")
	cat("mu     size = ",size(modcur$mu),"\n")
	cat("sig2   size = ",size(modcur$sig2),"\n")
	cat("alpha  size = ",size(modcur$alpha),"\n")
	cat("theta  size = ",size(modcur$theta),"\n\n")
}
```

## mu
```{r}
# oma is outer margin, for letting space to the general title
par(mfrow=c(2,4),mar=c(2,2,2,2), mgp=c(1.5,0.5,0),oma=c(0,0,2,0))
time = sample(time_span,1)
for(hh in 1:length(models_vector)){
	m.n <- as.numeric(strsplit(models_vector[hh], "")[[1]][c(2,4,6)])
	header <- bquote(eta[1]*  .(ifelse(m.n[1]==1,":Yes",":No"))*","~
    	             phi[1]*  .(ifelse(m.n[2]==1,":Yes",":No"))*","~
        	         alpha[t]*.(ifelse(m.n[3]==1,":Yes",":No")))

	
	plot(models.out[[hh]]$mu[time,sampled_station,],main=header,
		 xlab="",ylab="",type="l",cex.axis=0.8)
}
mtext(bquote("Trace plots of "*mu* " at time " * .(time) *", station " * .(sampled_station_name))
	  , side = 3, line = 0, outer = TRUE)
```

## sigma2
```{r}
# oma is outer margin, for letting space to the general title
par(mfrow=c(2,4),mar=c(2,2,2,2), mgp=c(1.5,0.5,0),oma=c(0,0,2,0))

time = sample(time_span,1)
for(hh in 1:length(models_vector)){
	m.n <- as.numeric(strsplit(models_vector[hh], "")[[1]][c(2,4,6)])
	header <- bquote(eta[1]*  .(ifelse(m.n[1]==1,":Yes",":No"))*","~
    	             phi[1]*  .(ifelse(m.n[2]==1,":Yes",":No"))*","~
        	         alpha[t]*.(ifelse(m.n[3]==1,":Yes",":No")))

	plot(models.out[[hh]]$sig2[time,sampled_station,],main=header,
		 xlab="",ylab="",type="l",cex.axis=0.8)
}
mtext(bquote("Trace plots of "*sigma^2* " at time " * .(time) *", station " * .(sampled_station_name))
	  , side = 3, line = 0, outer = TRUE)
```

## alpha
```{r}
# oma is outer margin, for letting space to the general title
par(mfrow=c(2,4),mar=c(2,2,2,2), mgp=c(1.5,0.5,0),oma=c(0,0,2,0))

time = sample(time_span,1)
for(hh in 1:length(models_vector)){
	m.n <- as.numeric(strsplit(models_vector[hh], "")[[1]][c(2,4,6)])
	header <- bquote(eta[1]*  .(ifelse(m.n[1]==1,":Yes",":No"))*","~
    	             phi[1]*  .(ifelse(m.n[2]==1,":Yes",":No"))*","~
        	         alpha[t]*.(ifelse(m.n[3]==1,":Yes",":No")))

	plot(models.out[[hh]]$alpha[,time],main=header,
		 xlab="",ylab="",type="l",cex.axis=0.8)
}
mtext(bquote("Trace plots of "*alpha* " at time " * .(time))
	  , side = 3, line = 0, outer = TRUE)
```



## theta
the params that generate the mu
```{r}
# oma is outer margin, for letting space to the general title
par(mfrow=c(2,4),mar=c(2,2,2,2), mgp=c(1.5,0.5,0),oma=c(0,0,2,0))

time = sample(time_span,1)
for(hh in 1:length(models_vector)){
	m.n <- as.numeric(strsplit(models_vector[hh], "")[[1]][c(2,4,6)])
	header <- bquote(eta[1]*  .(ifelse(m.n[1]==1,":Yes",":No"))*","~
    	             phi[1]*  .(ifelse(m.n[2]==1,":Yes",":No"))*","~
        	         alpha[t]*.(ifelse(m.n[3]==1,":Yes",":No")))

	plot(models.out[[hh]]$theta[,time],main=header,
		 xlab="",ylab="",type="l",cex.axis=0.8)
}
mtext(bquote("Trace plots of "*theta* " at time " * .(time))
	  , side = 3, line = 0, outer = TRUE)
```



# Metrics table
WAIC and LPML values.

```{r}
load("../data/Federico/drpm_comparison.Rdata")
```


```{r}
# Create table that contains the WAIC and LPML values
lpml <-  waic <- numeric()
amn <- matrix(NA, nrow = length(models.out), ncol=ncol(y_fit))
for(j in 1:length(models.out)){
	lpml[j] <- models.out[[j]]$lpml
  # lpmlr[j] <- lpml.robust(models.out[[j]]$llike)
	waic[j] <- models.out[[j]]$waic
	# amn[j,] <- round(apply(models.out[[j]]$alpha,2,mean),2)
}
res <- data.frame(names=names(models.out), lpml=lpml, waic=waic)
res[order(res[,2],decreasing = T),]
res = res[order(res[,2],decreasing = T),]
```


```{r}
library(xtable) # for latex table generation
xtable(res[order(res[,2],decreasing = T),],digits=2)
```
Sembrano essere migliori i modelli senza eta, cioè senza la parte autoregressive nelle Yt.
Anche se un po' di correlazione sembra esserci.
```{r}
par(mar=c(4,4,3,2))
acf(df_wsc$AQ_pm10,main="ACF plot of PM10")
```


```{r}
ordered_names = res$names[order(res[,2])]
order_best = order(res[,2],decreasing = T)

# s0_order = c()
# for (i in order_best){
# 	if(length(grep("S0",res$names[i],value=TRUE))>=1){
# 		s0_order = c(s0_order,i) 	
# 	}
# }
# s0_order

# s1_order = c()
# for (i in order_best){
# 	if(length(grep("S1",res$names[i],value=TRUE))>=1){
# 		s1_order = c(s1_order,i) 	
# 	}
# }
order_best
```



# Lagged ARI plots

```{r,warning=FALSE}
library(fields)
library(salso)
library(drpm)
library(MCMCpack)
library(mclust)
library(gstat)

# Compute the lagged partitions for all 16 models
ARImats <- vector("list", length(models.out))
for (i in 1:length(models.out)) {
  ARImats[[i]] <- matrix(NA, nrow=tps, ncol=tps)
}

for(h in 1:length(models.out)){
	rho = list()
	for(k in 1:tps){
		rho[[k]] <- salso(t(models.out[[h]]$Si[k,,]), loss="binder")
	}

	for(k in 1: tps){
		for(kk in 1: tps){
			ARImats[[h]][k,kk] <- adjustedRandIndex(rho[[k]], rho[[kk]])
		}
	}
}

pch=as.character(1:nrow(y))

# This is Figure 5 in the paper. 
# Lagged ARI plots for the tested models
ord2 = order_best

```


```{r,warning=FALSE}
# pdf(paste0("./figures/Federico/LaggedARI_comparison.pdf"), height=7, width=13)
par(mfrow=c(2,4),mar=c(2,2,2,4), mgp=c(1.5,0.5,0),oma=c(0,0,2,0))
	for(h in ord2){
		m.n <- as.numeric(strsplit(models_vector[h], "")[[1]][c(2,4,6)])
		header <- bquote(eta[1]*  .(ifelse(m.n[1]==1,"=Yes","=No"))*","~
	    	             phi[1]*  .(ifelse(m.n[2]==1,"=Yes","=No"))*","~
	        	         alpha[t]*.(ifelse(m.n[3]==1,"=Yes","=No")))
		image.plot(ARImats[[h]], main=header, 
				   #zlim=range(do.call(c,ARImats),na.rm=TRUE)
				   axes=FALSE,
				   col=rev(colora(80,56,0)),breaks=seq(0,1,length.out=81))
		mtext(text=c(paste("",1:tps)), side=2, line=0.3,
			  at=seq(0,1,length=max(time_span)), las=1, cex=0.6)
		mtext(text=c(paste("",1:tps)), side=1, line=0.3,
			  at=seq(0,1,length=max(time_span)), las=1, cex=0.6)
	}
mtext(bquote("Lagged ARI plots for the fitted models")
	  , side = 3, line = 0, outer = TRUE)
# dev.off()
```

# Best model analysis
```{r}
load("../data/drpm_comparison.Rdata")
drpm1 = models.out$out_E0P1A1_AR1
```


```{r,warning=FALSE}
df_cluster = data.frame(Longitude=c(),Latitude=c(),values=c(),clusters=c(),Time=c())
for(time in time_span){

	salso_out <- salso(t(drpm1$Si[time,,]),loss="binder")
	
	df_temp = data.frame(
		Longitude = sites$longitude,
		Latitude = sites$latitude,
		clusters = salso_out[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster = rbind(df_cluster,df_temp)
	
	
	
	# clusters log
	clusters_now = df_temp$clusters
	# n_clusters = max(clusters_now)
	n_clusters = unique(clusters_now)
	ycurrent = y[,paste0("w",time)]
	cat(crayon::red("Time",time,"\n"))
	for (cl in n_clusters){
		cat("Cluster",cl,"- size",length(ycurrent[which(clusters_now==cl)]),
			"- mean",mean(ycurrent[which(clusters_now==cl)]),"\n")
			
	}
}
```

```{r}
cols = colora(12,"div")[-2]
# cols chosen previously
clusters_old = NULL
for(time in time_span[1:4]){
	cat(crayon::red("Time",time,"\n"))
	
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now,very_verbose = 0)
	df_cluster_cut$clusters = clusters_now
	
	q = get_graph_plot(df_cluster_cut,titolo="mio titolo")
	
	print(q)
	clusters_old = clusters_now
}
```

```{r}
clusters_old = NULL
for(time in time_span[1:5]){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now
	
	p = get_boxplot_plot(df_cluster_cut)
	
	print(p)
	clusters_old = clusters_now
} # end for(time in eccc)
```

