---
title: "R Notebook"
output: html_document
---

```{r,warning = FALSE}
library(drpm)
library(salso)

# preparation
source("include.R") # for having df_agri
source("plot functions/plotter.R")

sites = data.frame(
	longitude = unique(df_weekly$Longitude), 
	latitude = unique(df_weekly$Latitude))
```

better to leave this alone (less buggy but dont know why).
```{r}
source("include_clusters_functions.R")
```


# create a pm10 table (station x time)
```{r}
stations = unique(df_wsc$IDStations)
y=data.frame()

for(st in stations){
  y_we_pm10=cbind(as.data.frame(st),t(df_wsc[which(df_wsc$IDStations==st),"AQ_pm10"]))
  y=rbind(y,y_we_pm10)
}

rownames(y) = NULL
colnames(y)<- c("id",paste0("w", 1:53))
df_wsc
y
```


# Trend plots

```{r}
yred=y[,2:54]
cols = colora(size(yred)[1],56,0)
for(i in 1:size(yred)[1]){
   if(i==1){
     plot(1:size(yred)[2],yred[i,],col=cols[i],ylim=extrema(yred),type='l',xlab='weeks',ylab='pm10')
 	  } 
	  else{
		  lines(1:size(yred)[2],yred[i,],col=cols[i])
	  }
}
```

```{r}
cols = colora(105,56,show=F)
chosen_variable_name = "AQ_pm10"

trendYearStation_week <- function(file_name){

	data_from_to = df_wsc
	len_time = 54
	
	chosen_variable = (data_from_to[,chosen_variable_name])

	# Crea il grafico ggplot
	station_trend <- ggplot(data_from_to,aes(x = week, 
												 y = AQ_pm10,
												 group=IDStations, 
												 color = as.factor(IDStations))) +
		
		geom_line(show.legend = FALSE) +
		labs(x = "Stations", y = chosen_variable_name, title = "Year: 2018 all stations") +
		ylim(range(na.omit(chosen_variable))) +
		scale_color_manual(values = cols) +
		theme_bw()+
		theme(panel.grid = element_blank()) +
		guides(color = guide_legend())+
		labs(x="week")
	
	len_time = (len_time%/%5)
	return(trend_animator(file_name,station_trend, data_from_to$week,len_time))
}
trendYearStation_week("None")
```



# Model fit

## Scaling/Centering update
```{r}
time_span = 1:6 # low time span for quick testing, real one will be 1:53

### authors suggested to/did scale the spatial locations and also centered the observations
y_fit = y[,1+time_span]
y_fit

### and for the scaling of spatial locations
std_sites = data.frame(
	longitude = unique(df_wsc$Longitude), 
	latitude = unique(df_wsc$Latitude))

plot(sites)
plot(std_sites)
```

## Fit
Burn in needs to be >= 10000. This after some long fits with low nburn (to see the whole behaviour of the MCMC) where there are some relevant changes even after 10000 iterations. So a lot of them needs to be discarded. I would set burn in to also 20000 maybe.

```{r}
niter=30000; nburn=100; nthin=2
nout <- (niter-nburn)/nthin
cat(nout,"valid iterations\n")
```

```{r}
seed_choice = runif(1)
set.seed(seed_choice)
cat("seed",seed_choice,"\n==========================\n",date(),"\n\n")
tempo_inizio <- Sys.time()
drpm1 <- drpm_fit(y=y_fit, 
		 s_coords = std_sites,
         M=1,
         initial_partition = NULL,
         starting_alpha = 0.5,
         unit_specific_alpha = FALSE,
         time_specific_alpha = TRUE, # meaning a bit ambiguos
		# Ok after experimenting it means that:
		# - if true we let alpha be a param that changes over time. 
		#	At time 1 we have a chain with some behaviour, 
		#	at time 2 another chain with another behaviour, ecc
		# - if false we instead fix alpha, ie all chains of all times
		#	will be the same, as they refer to the same parameter estimation
		# The authors in their tests set it to false, ie the fixed alpha

         alpha_0=FALSE,
         eta1_0=FALSE,
         phi1_0=FALSE,

         # modelPriors=c(0,100^2,1,1,1,1), # original default one
         modelPriors=c(0,100,10,5,5,2,2,1), # author suggestion/used one

		 # così con 1,1 è una uniforme
         alphaPriors=rbind(c(1,1)), # if time_specific_alpha == TRUE
         # alphaPriors=matrix(rep(c(1,1),105),105,2), # if unit_specific_alpha == TRUE
         # alphaPriors=matrix(rep(c(1,1),105),105,2), # if both the above are TRUE

         simpleModel = 0,
         theta_tau2 = c(0, 2), # only used if simpleModel=1

         # SpatialCohesion=3, # auxiliary similarity
         SpatialCohesion=4, # double dipper similarity, default one

         # cParms=c(0, 1, 2, 1), # default one
         cParms=c(0, 1, 5, 1), # author suggestion/used one (with 5)
		
         # mh=c(0.5,1,0.1, 0.1, 0.1), # default one
		 mh=c(0.1,0.1,0.4, 0.1, 0.1), # with a bit of author suggestion/used one

         verbose=TRUE,

         # draws=1100,burn=100,thin=1) # quick one
         # draws=31000,burn=1000,thin=1) # for trace plot analysis
         # draws=8000,burn=3000,thin=5) # a bit more serious seriou one
         # draws=10000,burn=2000,thin=8) # more serious one
         draws=niter,burn=nburn,thin=nthin) # adaptable one

tempo_fine <- Sys.time()
differenza_tempo <- tempo_fine - tempo_inizio
cat(crayon::cyan("Fit took:\n"))
print(round(differenza_tempo,digits = 4))

cat(crayon::blue("That was for fitting",max(time_span),"time steps.\nSo for fitting all 53 weeks the expected time with these parameters will be:\n"))
print(round(differenza_tempo/max(time_span)*53,digits=4))

cat(crayon::red("\nLPML =",drpm1$lpml, "\nWAIC =",drpm1$waic))
```


```{r}
# save(drpm1,file="../data/fit_serious.Rdata")
```

Fittig seriously, and on 30 weeks
LPML = 1860.18778637473 
WAIC = -4121.29141752817

Again on 30 weeks but quicker show less fitting goodness
LPML = 1370.56163617035 
WAIC = -3002.68219081088

Better (using 4 as dof in NIG)
ma il fit non era su tutte le settimane, era sulle prime 6
LPML = 304.537399598655 
WAIC = -702.001549273177

Worse (using 5 as dof in NIG)
ma il fit non era su tutte le settimane, era sulle prime 6
LPML = 285.202489478406 
WAIC = -646.215550051243


```{r}
names(drpm1)
# size(drpm1$Si)
# questa cos ha le simulazioni dei cluster assegnati
# ha dimensione 53 righe (o meno se fittiamo su meno tempi per dei test),
# poi ha 105 colonne, e 1000 "volte", perché
# - per ognuna delle 1000 iterazioni delle MCMC
# - dà i cluster assegnati dalla simulazione per le stazioni in quella simulazione


# the row dimensione will be 53, for now is time_span limit (like 5)
cat("\nSi     size = ",size(drpm1$Si),"\n")
cat("gamma  size = ",size(drpm1$gamma),"\n")
cat("mu     size = ",size(drpm1$mu),"\n")
cat("sig2   size = ",size(drpm1$sig2),"\n")
cat("alpha  size = ",size(drpm1$alpha),"\n")
cat("theta  size = ",size(drpm1$theta),"\n")
cat("tau2   size = ",size(drpm1$tau2),"\n")
cat("eta1   size = ",size(drpm1$eta1),"\n")
cat("phi0   size = ",size(drpm1$phi0),"\n")
cat("phi1   size = ",size(drpm1$phi1),"\n")
cat("lam2   size = ",size(drpm1$lam2),"\n")
cat("llike  size = ",size(drpm1$llike),"\n")
cat("fitted size = ",size(drpm1$fitted),"\n")
```



# Trace plots?
```{r}
sampled_station = floor(runif(1,1,105))
cat("sampled_station =",sampled_station,"- that is station called",unique(df_wsc$IDStations)[sampled_station])
sampled_station_name = unique(df_wsc$IDStations)[sampled_station]

```

## alpha
It depends:
- if time_specific_alpha = FALSE we get the same MCMC, ie the same plots
- if time_specific_alpha = TRUE we get different MCMC, alpha behaviour changes in time
- if unit_specific_alpha = ecc but we dont use this option
```{r}
dim(drpm1$alpha)
```
```{r}
if(len(size(drpm1$alpha))==2){ # alpha is not unit dependent
	for (time in time_span){
	# cat("Week",time,"- alpha mean value =",mean(drpm1$alpha[,time]),"\n")
	plot(drpm1$alpha[,time],type="l",
		 main=bquote("Trace plot of " * alpha[.(time)] 
		 * " (mean value = " * .(mean(drpm1$alpha[,time])) * ")"
		 ),
		 xlab = "MCMC iterations",ylab="values")
	}
}

if(len(size(drpm1$alpha))==3){ # alpha is unit dependent 
	for (time in time_span){
	plot(drpm1$alpha[time,sampled_station,],type="l",
		 main=bquote("Trace plot of " * alpha[.(time)] * " - station" * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
	}
}
```

## Si
There are MCMC with time and with stations.
```{r}
dim(drpm1$Si)
```
```{r}
for (time in time_span){
	plot(drpm1$Si[time,sampled_station,],type="l",
		 main=bquote("Trace plot of partition "*rho* " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
```

## gamma
Gamma is not really a parameter but the collection of the alphas.
So we dont care abouth her trace plot.

## mu
Same as Si, there are MCMC with time and with stations.
```{r}
dim(drpm1$mu)
```
```{r}
for (time in time_span){
	plot(drpm1$mu[time,sampled_station,],type="l",
		 main=bquote("Trace plot of " * mu * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span){
	par(mar=c(4,4,3,2))
	acf(drpm1$mu[time,sampled_station,],main=bquote("ACF plot of " * mu * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)))
}
```

## sigma2
Same as mu and Si
```{r}
dim(drpm1$sig2)
```
```{r}
for (time in time_span){
	plot(drpm1$sig2[time,sampled_station,],type="l",
		 main=bquote("Trace plot of "* sigma^2 * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span){
	par(mar=c(4,4,3,2))
	acf(drpm1$sig2[time,sampled_station,],main=bquote("ACF plot of " * sigma^2 * " at week " * .(time) * 
		 				" - station " * .(sampled_station_name)))
}
```

## theta
MCMC for each time, one for all stations.
```{r}
dim(drpm1$theta)
```
```{r}
for (time in time_span){
	plot(drpm1$theta[,time],type="l",
		 main=bquote("Trace plot of " * theta * " at week "*.(time)),
		 xlab = "MCMC iterations",ylab="values")
}
for (time in time_span){
	par(mar=c(4,4,3,2))
	acf(drpm1$theta[,time],main=bquote("ACF plot of " * theta * " at week "*.(time)))
}
```


## tau2
MCMC for each time, one for each station.
```{r}
dim(drpm1$tau2)
```
```{r}
for (time in time_span){
	plot(drpm1$tau2[,time],type="l",
		 main=bquote("Trace plot of " * tau^2 * " at week "*.(time)),
		 xlab = "MCMC iterations",ylab="values")	
}
```

## eta1
MCMC for each station, no time involved
```{r}
dim(drpm1$eta1)
```
```{r}
plot(drpm1$eta1[,sampled_station],type="l",
	 main=bquote("Trace plot of " * eta[1] *" - station " * .(sampled_station_name)),
	 xlab = "MCMC iterations",ylab="values")	
```

## phi0
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$phi0)
```
```{r}
plot(drpm1$phi0[,1],type="l",
	 main=bquote("Trace plot of "* phi[0]),
	 xlab = "MCMC iterations",ylab="values")
```

## phi1
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$phi1)
```
```{r}
plot(drpm1$phi1[,1],type="l",
	 main=bquote("Trace plot of "* phi[1]),
	 xlab = "MCMC iterations",ylab="values")
```

## lambda2
MCMC no time involved and no stations involved.
That's because they are just part of AR structure of the model.
```{r}
dim(drpm1$lam2)
```
```{r}
plot(drpm1$lam2[,1],type="l",
	 main=bquote("Trace plot of "* lambda^2),
	 xlab = "MCMC iterations",ylab="values")
```



# Map cluster plots
## dataframe for clusters
```{r,warning=FALSE}
df_cluster = data.frame(Longitude=c(),Latitude=c(),values=c(),clusters=c(),Time=c())
for(time in time_span){

	salso_out <- salso(t(drpm1$Si[time,,]),loss="binder")
	
	df_temp = data.frame(
		Longitude = sites$longitude,
		Latitude = sites$latitude,
		clusters = salso_out[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster = rbind(df_cluster,df_temp)
	
	
	
	# clusters log
	clusters_now = df_temp$clusters
	# n_clusters = max(clusters_now)
	n_clusters = unique(clusters_now)
	ycurrent = y[,paste0("w",time)]
	cat(crayon::red("Time",time,"\n"))
	for (cl in n_clusters){
		cat("Cluster",cl,"- size",length(ycurrent[which(clusters_now==cl)]),
			"- mean",mean(ycurrent[which(clusters_now==cl)]),"\n")
			
	}
}
```



## ARI plot
```{r}
library(mclust)
##########################
FIT = drpm1 # your fit
LEN = max(time_span)
##########################

# build the ARI matrix
ARImats <- matrix(NA, nrow=LEN, ncol=LEN)
rho_ARI <- list()
for(k in 1:LEN){
	rho_ARI[[k]] <- salso(t(FIT$Si[k,,]), loss="binder") # adjust with your fit $Si dimension
}
for(k in 1: LEN){
	for(kk in 1: LEN){
		ARImats[k,kk] <- adjustedRandIndex(rho_ARI[[k]], rho_ARI[[kk]])
	}
}
cols_ARI = colora(60,56,0)
# or see ?designer.colors for colors
library(fields)
image.plot(ARImats, main="Lagged ARI values",axes=FALSE,col=rev(cols_ARI))
mtext(text=c(paste("",1:LEN)), side=2, line=0.3,at=seq(0,1,length=LEN), las=1, cex=0.8)
mtext(text=c(paste("",1:LEN)), side=1, line=0.3,at=seq(0,1,length=LEN), las=1, cex=0.8)
```


# Clusters distribution

## cols choice
```{r}
# choose wisely
# this will be from now on the color palette decision
cols = colora(12,"div")[-2] # togliamo il giallino
# cols= colora(12,111)
```


## continuos
```{r,warning=FALSE}
clusters_old = NULL
for(time in time_span){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now
	
	p = get_hist_continuos_plot(df_cluster_cut,verbose=0)
	
	print(p)
	clusters_old = clusters_now
} # end for(time in eccc)
```

## histogram v1 - no fill
```{r,warning=FALSE}
clusters_old = NULL
for(time in time_span){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now
	
	p = get_hist_color_plot(df_cluster_cut)
	
	print(p)
	clusters_old = clusters_now
} # end for(time in eccc)
```

## histogram v2 - fill
```{r,warning=FALSE}
clusters_old = NULL
for(time in time_span){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now
	
	p = get_hist_fill_plot(df_cluster_cut)
	
	print(p)
	clusters_old = clusters_now
} # end for(time in eccc)
```

## boxplot
```{r}
clusters_old = NULL
for(time in time_span){

	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	df_cluster_cut$clusters = clusters_now
	
	p = get_boxplot_plot(df_cluster_cut)
	
	print(p)
	clusters_old = clusters_now
} # end for(time in eccc)
```

```{r}
img_lombardy <- readPNG(paste0(start_folder,"plot functions/italia/lombardia_cut.png"))
p = DefaultPlot(add_bg=T)
print(p)
```



# Plot for time 1
```{r}
df_cluster_cut = df_cluster[df_cluster$Time==time,]
p  <-  DefaultPlot()+
	geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude, color = factor(clusters)), size = 3)+
	labs(title = "Cluster map")+
		guides(color = guide_legend(title = "Clusters"))

p
```


## add bg image
background image of lombardy
```{r}
library(jpeg)
library(png)
# img <- readJPEG("./plot functions/italia/lombardia.JPG")
img <- readPNG("./plot functions/italia/lombardia_cut.png")

time=2
df_cluster_cut = df_cluster[df_cluster$Time==time,]
p  <-  DefaultPlot()+
	geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude,
										  color = factor(clusters)), size = 3)+
	labs(title = "Cluster map")+
	guides(color = guide_legend(title = "Clusters"))

print(p)
p  <-  DefaultPlot()+background_image(img)+
	geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude,
										  color = factor(clusters)), size = 3)+
	labs(title = "Cluster map")+
	guides(color = guide_legend(title = "Clusters"))

print(p)

```



# Save png(s) for animation
```{r}
save_pngs = 0

if(save_pngs==1){
for( time in time_span){
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	
	p  <-  DefaultPlot()+
		geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude, 
											  color = factor(clusters)), size = 3)+
		labs(title = "Cluster map")+
		guides(color = guide_legend(title = "Clusters"))
	
	ggsave(
	  paste0("cluster_plots/cluster_time-",time,".png"),
	  plot = p
	)
}
} else {
	cat("Not saving pngs for now.")
}
```


# Fede: graph cluster plot

## Version 2 - final
all the functions are in the include_clusters_function. Here is the code to plot.
```{r}
# cols chosen previously
clusters_old = NULL
for(time in time_span){
	cat(crayon::red("Time",time,"\n"))
	
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now,very_verbose = 0)
	df_cluster_cut$clusters = clusters_now
	
	q = get_graph_plot(df_cluster_cut)
	
	print(q)
	clusters_old = clusters_now
}
```



```{r}
# cols chosen previously
clusters_old = NULL
for(time in time_span){
	cat(crayon::red("Time",time,"\n"))
	
	df_cluster_cut = df_cluster[df_cluster$Time==time,]
	clusters_now = df_cluster_cut$clusters
	# clusters_now = mode_correct_clusters(clusters_old,clusters_now,very_verbose = 0)
	df_cluster_cut$clusters = clusters_now
	
	q = get_graph_plot(df_cluster_cut)
	
	print(q)
	clusters_old = clusters_now
}
```
Forse possiamo fare insieme questa mappa con quella degli istogrammi sopra.
Così ad ogni istante temporale, e poi nell'animazione, vediamo sia i cluster sia quanto sono diversi in termini di "densità".

Del tipo
```{r}
library(gridExtra)
library(grDevices) # for png saving

clusters_old = NULL
for(time in time_span){

# GRAPH #######################
cat(crayon::red("Time",time,"\n"))
df_cluster_cut = df_cluster[df_cluster$Time==time,]
clusters_now = df_cluster_cut$clusters
clusters_now = mode_correct_clusters(clusters_old,clusters_now)
df_cluster_cut$clusters = clusters_now

	cur_num = sprintf("%02d", time)
	png(filename=paste0("./cluster_plots/test/graph_plot_",cur_num,".png"), width=1000, height=600)
	plot_graph_and_hist(df_cluster_cut)
	dev.off()
	# ggsave(file=paste("./cluster_plots/test/graph_plot_",time,".png"), width=4, height=4, dpi=300)


clusters_old = clusters_now
}
```



# Gif creation in R test
```{r}
# Carica i pacchetti
library(magick)
library(animation)

## list file names and read in
percorso = "./cluster_plots/test/"
imgs <- list.files(path = percorso, pattern = ".png", full.names = TRUE)
img_list <- lapply(imgs, image_read)

## join the images together
img_joined <- image_join(img_list)

## animate at 2 frames per second
img_animated <- image_animate(img_joined, fps = 2)

## view animated image
# img_animated

## save to disk
image_write(image = img_animated,
            path = paste0(percorso,"test.gif"))
```



