---
title: "na exploration"
output: html_notebook
---

Still haven't removed columns / modified / created new dataset
Code should be robust enough to work on the merged dataset and modify that directly
Some considerations as comments below graphs


```{r}
library(naniar)
library(hash)
library(assert)
library(ggplot2)
library(UpSetR)
library(visdat)

source("include.R")
```

Visualize dataset and summary
```{r}
# dati = read.csv("Agrimonia_Dataset_v_3_0_0.csv")
dati = df_agri
head(dati)
dim(dati)
summary(dati)
```
Count of na for each column
```{r}
sum(is.na(dati))  
nas = sapply(dati,function(x) sum(is.na(x)))
barplot(nas[nas>0],las=2)
```


plot na for columns to see if there is any pattern
```{r}
# x11()  #too big of a graph for the notebook
dev.new()
vis_miss(dati,warn_large_data = FALSE)
```
#can see different patterns ->
#blocks for some of the AQ variables  -> would remove
#regular "stripes" on the EM variables  -> see how useful/sparse the problem is
#stripes and then a block at the bottom for the soil use var  -> would remove



Grouping by station, plot from library UpSet
```{r}
gg_miss_fct(x = dati,fct = IDStations)
```
Messy plot but plotted faster than the one before
Stations are on the horizontal axis



Try with dataset divided by station
```{r}
dati = df_agri # loade on top by include.R
df_stat=hash()
stations = unique(dati$IDStations)
print(stations)

for (st in stations){
  df_stat[[st]] = dati[which(dati$IDStations == st),]
  assert(dim(df_stat[[st]])[1] == 2192) # make sure each df_stat has all his 2192 obs
}

```
Visualize if all ok
```{r}
#example
dati_1264=df_stat[["1264"]]
dim(dati_1264)
head(dati_1264)
```

Graph as before for each and all of the stations to see if any has interestingly distributed missing values
```{r}
NSTAT = 5 # 141 if want to see them all

for (st in stations[1:NSTAT]){
  # df_stat[[st]] = dati[which(dati$IDStations == st),]
  # assert(dim(df_stat[[st]])[1] == 2192) # make sure each df_stat has all his 2192 obs
	
  # sometimes it didnt work for me so i am just proving different options here
  # plot(vis_miss(df_stat[[st]],warn_large_data = FALSE)) #a plot for each station
  plot(vis_miss(as.data.frame(df_stat[[st]]),warn_large_data = FALSE)) #a plot for each station
}
```


#can see graphically for every variable
#notice how for some stations EM have na only on last year or so
#We could substitute with mean or median for EM variables using mean of first years of same station but risk losing temporal changing -> maybe not good idea (?)


With another plot
```{r}
gg_miss_var(dati,show_pct = TRUE)
```


Plot to see combinations of variables with the most na
```{r}
gg_miss_upset(dati,nsets = 10)
```










To do all graphs above with a single function on the dataset
```{r}
inspect_df_NA <- function(df){
  plot_list <- list()
  plot_list$miss_table <- vis_miss(df,warn_large_data = FALSE)    
  plot_list$interceptions <- gg_miss_upset(df,nsets = 10)
  plot_list$heatmap <- gg_miss_fct(x = df,fct = IDStations)
  plot_list$percentage <- gg_miss_var(df, show_pct = TRUE)

  return(plot_list)
}
```

```{r}
plots <- inspect_df_NA(dati)

plots$miss_table
plots$heatmap
plots$interceptions
plots$percentage
```
