---
title: "R Notebook"
output: html_notebook
---

```{r}
source("include.R")
```

```{r}
cat("df_agri shape",size(df_agri),"\n")
cat("df_2018 shape",size(df_2018),"\n")
```

# NA Filling ideas

We have to choose which approach to use:
- historical fill ("if a monday is missing fill it with the mean/median of all mondays")
- temporal interpolation ("if a monday is missing fill it with the mean of sunday and tuesday")
or others approach if you have.

We could inspect the trend to see which approach is better.

```{r}
# add column day (names) on df_2018
days = c("lunedì","martedì","mercoledì","giovedì","venerdì","sabato","domenica")
day_names = weekdays(df_2018$Time)
df_2018$day = as.factor(day_names)
head(df_2018)
```


## Trend inspection - historical fill
Here with historical fill we mean that when we encounter a NA value we do this
- see at which day of the week corrsponds that value
- look up the mean for that day values (mean of mondays, mean of tuesdays, ecc)
- substitute the NA with that day mean
Ie if a value is missing, and that NA occurred on a monday, then we look up the mean over all the mondays, and substitute that NA with that monday mean.

Maybe we should also try with a week-mean substitution, but this is basically what the next idea, temporal filling, does.

```{r}
# cols = colora(7,runif(1,0,133),1)
cols = colora(7,24,0)
st = sample(unique(df_2018$IDStations),1)

for (d in days){
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station
	df_st_day = df_st[df_st$day == d,] # filter a certain day
	
	col_idx = which(days==d)
	if(col_idx==1)
		plot(df_st_day$AQ_pm10,xlab="year weeks",ylab="PM10 values",
			 main=paste("station",st),col=cols[col_idx],type="l")
	else
		points(df_st_day$AQ_pm10,xlab="year weeks",ylab="PM10 values",
			   main=paste("station",st),col=cols[col_idx],type="l")
}
legend("top",c("lunedì","martedì","mercoledì","giovedì","venerdì","sabato","domenica"),
	   fill=cols,cex=0.6,bty = "n")
```

It seems that there is the U trend (high in winter, low in summer), as we already knew.
So maybe averaging does not lead to a good result, as we will put "high" values in summer and "low" values in winter, as the next plot shows.

```{r}
# cols = colora(7,runif(1,0,133),1)
cols = colora(7,24,0)
st = sample(unique(df_2018$IDStations),1)

for (d in days){
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station
	df_st_day = df_st[df_st$day == d,] # filter a certain day
	
	col_idx = which(days==d)
	if(col_idx==1)
		plot(df_st_day$AQ_pm10,xlab="year weeks",ylab="PM10 values",
			 main=paste("station",st),col=cols[col_idx],type="l")
	else
		points(df_st_day$AQ_pm10,xlab="year weeks",ylab="PM10 values",
			   main=paste("station",st),col=cols[col_idx],type="l")
	
	abline(h=mean(na.omit(df_st_day$AQ_pm10)),col=cols[col_idx])
}
legend("top",c("lunedì","martedì","mercoledì","giovedì","venerdì","sabato","domenica"),
	   fill=cols,cex=0.6,bty = "n")
```

## Trend inspection - temporal interpolation
or "intempolation" :)

Now the idea is to see how much variability there is in consequent days, to see if it's feasible to subsitute a NA with like an interpolation of the closest not-NA values around him.

So for now we select a random interval of time and see the trend there, and compare it with the reconstruction we would obtain with this temporal interpolation idea.


```{r}
interpola_NA <- function(obs) {
  non_na_indices <- which(!is.na(obs))
  na_indices <- which(is.na(obs))
  # print(non_na_indices)
  # print(na_indices)
  
  # loop on Na indices
  for (na_index in na_indices) {
    # Trova l'indice più vicino a sinistra e quello più vicino a destra
    left_index <- suppressWarnings(max(non_na_indices[non_na_indices < na_index]))
    right_index <- suppressWarnings(min(non_na_indices[non_na_indices > na_index]))
    # cat("NA idx",na_index," - LR values = ",obs[left_index],",",obs[right_index],"\n")

    # Esegui l'interpolazione se ci sono valori a sinistra e a destra
    if (!is.na(left_index) && !is.na(right_index)) {
      left_value <- obs[left_index]
      right_value <- obs[right_index]
      
      # Calcola il valore interpolato
      interpolated_value <- left_value + 
        ((right_value - left_value) / (right_index - left_index)) * (na_index - left_index)
      
      # Sostituisci il valore NA con quello interpolato
      obs[na_index] <- interpolated_value
    }
    if(is.na(obs[na_index])){
    	obs[na_index] = na.omit(c(obs[left_index],obs[right_index]))
    }
	# cat(obs[na_index],"\n")
  }
  return(obs)
}

# example
test <- c(NA,NA,10, 15, NA, 20, 24, 20, 18, NA, NA, 10, 9, 9, NA)
print(test)
result <- interpola_NA(test)
print(round(result))
```

```{r}
# to not have huge intervals
we_have_na = 0
while(we_have_na == 0){
	end_day = 400
	while(end_day > 365){
		start_day = round(runif(1, min=0, max=365))
		end_day = start_day + round(runif(1,min=5,max=30))
	}
	
	title=paste(end_day-start_day,"days:",
				"from",format(as.Date("2018-01-01")+start_day),
				"to",format(as.Date("2018-01-01")+end_day))
	
	
	# st = "635"
	st = sample(unique(df_2018$IDStations),1)
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station
	df_st_int = df_st[start_day:end_day,]
	we_have_na = sum(as.numeric(is.na(df_st_int$AQ_pm10)))
}

plot(df_st_int$Time,df_st_int$AQ_pm10,main=title,type="b",lwd=2)
obs = df_st_int$AQ_pm10
obs_wo_na = interpola_NA(obs)

df_st_int_wo_na = df_st_int
df_st_int_wo_na$AQ_pm10 = obs_wo_na
lines(df_st_int_wo_na$Time,df_st_int_wo_na$AQ_pm10,type="b",lty=2,col="blue")
```
This seems a better choice for NA filling.
We proceed with a comparison now.

## Comparison of the two approaches
```{r}
historic_fill_pm10col_na = function(df_st){
	day_names = as.vector(df_st$day)
	obs = df_st$AQ_pm10
	day_mean = hash()
	for (d in days){
		day_mean[[d]] = mean(na.omit(obs[day_names==d]))
	}
	for (i in 1:length(obs)){
		if(is.na(obs[i])){
			obs[i] = day_mean[[day_names[i]]]
		}
	}
	return(obs)
} 
```

### random time interval
```{r}
we_have_na = 0
while(we_have_na == 0){
	end_day = 400
	while(end_day > 365){
		start_day = round(runif(1, min=0, max=365))
		end_day = start_day + round(runif(1,min=10,max=40))
	}
	st = sample(unique(df_2018$IDStations),1)
	title=paste("station",st,"-",
				end_day-start_day,"days:",
				"from",format(as.Date("2018-01-01")+start_day),
				"to",format(as.Date("2018-01-01")+end_day))
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station
	df_st_int = df_st[start_day:end_day,]
	we_have_na = any(is.na(df_st_int$AQ_pm10))
}
plt_type = "l"
plot(df_st_int$Time,df_st_int$AQ_pm10,main=title,type=plt_type,lwd=2)

############## Method 2 intempolation
obs = df_st_int$AQ_pm10
obs_wo_na = interpola_NA(obs)
df_st_int_wo_na = df_st_int
df_st_int_wo_na$AQ_pm10 = obs_wo_na
lines(df_st_int_wo_na$Time,df_st_int_wo_na$AQ_pm10,type=plt_type,lty=2,col="blue",lwd=0.6)

############## Method 1 historical fill

obs_wo_na = historic_fill_pm10col_na(df_st)
df_st_int_wo_na = df_st_int
df_st_int_wo_na$AQ_pm10 = obs_wo_na[start_day:end_day]
lines(df_st_int_wo_na$Time,df_st_int_wo_na$AQ_pm10,type=plt_type,lty=2,col="red",lwd=0.6)

legend("topright",c("intempolation","historical"),fill=c("blue","red"),bty="n")
```

### selected time interval
```{r}
start_day = 100
end_day = 300

cols = colora(3,56,0)
we_have_na = 0
while(we_have_na == 0){
	st = sample(unique(df_2018$IDStations),1)
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station

	df_st_int = df_st[start_day:end_day,]
	we_have_na = any(is.na(df_st_int$AQ_pm10))
}
title = paste("station",st,"- #NA =",sum(as.numeric(is.na(df_st_int$AQ_pm10))))
plt_type = "l"
plot(df_st_int$Time,df_st_int$AQ_pm10,main=title,lwd=1,type=plt_type,col=cols[1])

############## Method 2 intempolation
obs = df_st_int$AQ_pm10
obs_wo_na = interpola_NA(obs)
df_st_int_wo_na = df_st_int
df_st_int_wo_na$AQ_pm10 = obs_wo_na
lines(df_st_int_wo_na$Time,df_st_int_wo_na$AQ_pm10,type=plt_type,col=cols[2])

############## Method 1 historical fill

obs_wo_na = historic_fill_pm10col_na(df_st)
df_st_int_wo_na = df_st_int
df_st_int_wo_na$AQ_pm10 = obs_wo_na[start_day:end_day]
lines(df_st_int_wo_na$Time,df_st_int_wo_na$AQ_pm10,type=plt_type,col=cols[3])

# to superimpose the first color
lines(df_st_int$Time,df_st_int$AQ_pm10,main=title,lwd=1,type=plt_type,col=cols[1])
legend("topright",c("original","intempolation","historical"),fill=cols,bty="n")
```

### days trend fill comparison
```{r}
# cols = colora(7,runif(1,0,133),1)
cols = colora(3,56,0)

enough_na = 0
while(enough_na==0){
	st = sample(unique(df_2018$IDStations),1)
	df_st = df_2018[df_2018$IDStations==st,] # filter a single station
	enough_na = sum(as.numeric(is.na(df_st$AQ_pm10)))>20
}

for (d in days){
# d = "lunedì"
	df_st_day = df_st[df_st$day == d,] # filter a certain day

	plot(df_st_day$AQ_pm10,xlab="year weeks",ylab="PM10 values",
		 main=paste("station =",st,"- day =",d,"- #NA =",
		 		   sum(as.numeric(is.na(df_st_day$AQ_pm10)))),
		 col=cols[1],type="l")
	lines(interpola_NA(df_st_day$AQ_pm10),col=cols[2],type="l")
	lines(historic_fill_pm10col_na(df_st_day),col=cols[3],type="l")
	
	# to superimpose the first color
	lines(df_st_day$AQ_pm10)
	legend("top",c("original","intempolation","historical"),fill=cols,bty="n")
}

```


# NA cols filling
```{r}
for (c in colnames(df_2018)){
	cat(sprintf("%28s, %s\n",c,typeof(df_2018[,c])))
}
# type character: 
# ("WE_mode_wind_direction_10m","WE_mode_wind_direction_100m", "LI_pigs_v2","LI_bovine_v2")
# the first two are really characters, the last two no are numbers not correctly read by R

head(df_2018$LI_pigs_v2)
df_2018$LI_pigs_v2 = as.numeric(df_2018$LI_pigs_v2)
df_2018$LI_bovine_v2 = as.numeric(df_2018$LI_bovine_v2)
head(df_2018$LI_pigs_v2)
```

Candidate code for filling with the temporal interpolation idea.
```{r}
df_2018_filled = df_2018
for (c in colnames(df_2018)){
	cat(sprintf("%28s, #NAs = %f\n",c,sum(as.numeric(is.na(df_2018_filled[,c])))))
}
# we just have to fill AQ_pm10 and LI_ecc variables
```

```{r}
source("plot functions/plot_data_and_libraries.R")
suppressWarnings(source("plot functions/plot_utilities.R"))
```

```{r}
initial_date = "2018-01-01"
final_date = "2018-12-31"
chosen_stations = 1:5
file_name = "None"

for (chosen_variable_name in c("LI_pigs","LI_bovine","LI_pigs_v2","LI_pigs_v2")) {
	trendYearStation_plot <- trendYearStation(initial_date,final_date,chosen_stations,
											  file_name,chosen_variable_name)
}
# the temporal interpolation seems good here, the trend is very stable
```


# Week division
```{r}

```



