---
title: "R Notebook"
---

```{r,warning=FALSE}
source("include.R")
```

```{r,warning=FALSE}
source("plot functions/plot_functions.R")
```

# Istogram Y and ln(Y)

```{r}
cols = colora(2,15)
pm10 = df_agri$AQ_pm10
par(mfrow=c(1,2),mar=c(2,2,2,2))
hist(pm10,col=cols[1],probability = T)
hist(log(pm10),col=cols[2],probability = T,xlim=c(-1,6))
```


```{r}
# Istogramma della variabile originale
hist_original <- ggplot(data = data.frame(Y = Y), aes(x = Y, y=..density..)) +
  geom_histogram(binwidth = 7, fill = cols[1], color = "black", alpha = 0.7) +
  labs(title = "values of pm10", x = "", y = "") +
  theme_minimal()

# Istogramma del logaritmo della variabile
hist_log <- ggplot(data = data.frame(log_Y = log(Y)), aes(x = log_Y, y=..density..)) +
  geom_histogram(binwidth = 0.25, fill = cols[2], color = "black", alpha = 0.7) +
  labs(title = "values of ln(pm10)", x = "", y = "") +
  theme_minimal()+
  coord_cartesian(xlim = c(-0.5,6))

# Affiancamento dei due grafici
grid.arrange(hist_original, hist_log, ncol = 2)
```



# Mappa stazioni: REMOVE LEGEND
```{r}
stationPlot <- stationPlot()
```


```{r}
head(data_agc_lomb)
```

# Grid map with chosen variable 
```{r}
initial_date = "2016-01-01"
final_date = "2016-01-01"
every = "month"

# if you change the file_name from None it will create a mp4 video
file_name = "None"

data_agc_lomb$WE_wind_speed_10m_max = as.numeric(data_agc_lomb$WE_wind_speed_10m_max)
chosen_variable_name = "WE_wind_speed_10m_max"
# chosen_variable_name = "Altitude"
color_low =  "yellow"
color_high = "blue"

map = gridMap(initial_date,final_date,every,file_name,color_low,color_high,chosen_variable_name)
```


#  Map expanding radius: togliere la legenda

```{r}
initial_date = "2016-01-01"
final_date = "2016-12-01"
every = "month"

# if you change the file_name from None it will create a mp4 video
file_name = "prova expanding circles"

chosen_var_name = "AQ_pm10" 

circles_plot <- circlesPlot(initial_date,final_date,every,file_name,chosen_var_name)
```


# WIND  

```{r}
initial_date = "2016-01-01"
final_date = "2017-01-01"
every = "month"

# if you change the file_name from None it will create a mp4 video
file_name = "wind plot 2016"
wind = windPlot(initial_date,final_date,every,file_name)
```


# xy color+size in time
```{r}
var1_name = "AQ_no2"
var2_name = "WE_wind_speed_100m_mean"
# you can change size to refer to a particular variable
size_name = "LI_bovine"
size_name = 3
colors_factor_name = "IDStations"

xyplot <- xyPlot(initial_date,final_date,every,file_name,var1_name,var2_name,size_name,colors_factor_name)

```
# Trend plots
## 1 station - multiple years

```{r}
chosen_station = 1
final_date = "2021-12-31"
file_name = "time_trend"
chosen_variable_name = "AQ_pm10"

trendStationYear_plot = trendStationYear(chosen_station,initial_date,final_date,file_name,chosen_variable_name)
```



## 1 year - multiple stations
```{r}
initial_date = "2016-01-01"
final_date = "2016-12-31"
chosen_stations = 1:4
file_name = "prova trend year"
chosen_variable_name = "AQ_pm10"

trendYearStation_plot <- trendYearStation(initial_date,final_date,chosen_stations,file_name,chosen_variable_name)
```


# TO DO LIST:
- check trend plot animation (Time vs t)

- higher video quality mp4 av_renderer?
	for this maybe we just need to use the device parameter, and set it to "svg" as svg does
	not compress images. This is the device help of the animate package:
	The device to use for rendering the single frames.
	Possible values are 'png', 'ragg_png' (requires the ragg package), 'jpeg',
	'tiff', 'bmp', 'svg', and 'svglite' (requires the svglite package). (default 'png')

- crea grafici carini







