---
title: "Untitled"
output: html_document
---


```{r,warning=FALSE}
source("include.R") # why didnt you use it above, in your code? :'/
source("plot functions/plotter.R")
```

If we include this alone seems to work better (dont know why).
```{r}
source("include_clusters_functions.R")
```


```{r}
library(salso)
library(ppmSuite)
```

Sometimes it fails the execution (dont know why). In that case:
- go to the file include_clusters_function.R and run it all (ctrl+alt+R)
- come back here and now it should run finely

# gaussian_ppmx

## loop fit
```{r}
clusters_tm1 = NULL

for (time in 1:6){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y = df_time$AQ_pm10
	X = df_time[,-c(1:5,7)]

	fit = gaussian_ppmx(y, X=X, Xpred=NULL,
	                  meanModel=1,
	                  cohesion=1,
	                  M=1,
	                  PPM = FALSE,
	                  similarity_function=1,
	                  consim=1,
	                  calibrate=0,
	                  simParms=c(0.0, 1.0, 0.1, 1.0, 2.0, 0.1, 1),
	                  modelPriors=c(0, 100^2, 1, 1),
	                  mh=c(0.5, 0.5),
	                  draws=1100,burn=100,thin=1,
	                  verbose=FALSE)
	
	clusters = salso(fit$Si,loss="binder")
	clusters = clusters[1:105]
	### Mode correct clusters
	clusters_new = mode_correct_clusters(clusters_tm1,clusters)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	
	
	### Hist plot
	df_hist = data.frame(clust_vals=clusters[1:105],ycurrent=y)
	my_pad = 2
	n_clusters = max(clusters)
	p = ggplot(df_hist, aes(ycurrent, fill = factor(clust_vals)))+
		scale_fill_manual(values = colora(n_clusters,77,0),name="Cluster")+
		geom_density(alpha = 0.3)+
		ggtitle(paste("Time",time))+
		theme_classic()+
		xlim(extrema(y)+c(-my_pad,my_pad))
	print(p)
	
	
	
	### Graph plot
	clusters = df_cluster_cut$clusters
	edges = assemble_edges(clusters,need_to_debug=0)
	# edges
	p  <-  DefaultPlot()+
		geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude,
											  color = factor(clusters)), size = 2)+
		labs(title = paste("Cluster map - time",time))+
		guides(color = guide_legend(title = "Clusters"))
	
	q = p + geom_segment(aes(x = x, y = y, xend = xend, yend = yend,
						 color = cluster),
					 linewidth=1.2,
					 data = edges)
	# print(p)
	print(q)
	
	clusters_tm1 = clusters
} # end for time
```
# Model sppm

## loop fit
```{r}
clusters_tm1 = NULL

for (time in 1:5){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y = df_time$AQ_pm10
	s = data.frame(
		lat = unique(df_weekly$Latitude),
		long = unique(df_weekly$Longitude)
	)

	fit = sppm(y,s,
	    s.pred=NULL,
	    cohesion=3,
	    M=1,
	    modelPriors=c(0, 100^2, 10, 10),
	    cParms=c(1, 1.5, 0, 1, 2, 2),
	    mh=c(0.5, 0.5),
	    draws=1100,burn=100,thin=1)
	
	clusters = salso(fit$Si,loss="binder")
	clusters = clusters[1:105]
	### Mode correct clusters
	clusters = mode_correct_clusters(clusters_tm1,clusters)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	
	
	### Hist plot
	df_hist = data.frame(clust_vals=clusters[1:105],ycurrent=y)
	my_pad = 2
	n_clusters = max(clusters)
	p = ggplot(df_hist, aes(ycurrent, fill = factor(clust_vals)))+
		scale_fill_manual(values = colora(n_clusters,77,0),name="Cluster")+
		geom_density(alpha = 0.3)+
		ggtitle(paste("Time",time))+
		theme_classic()+
		xlim(extrema(y)+c(-my_pad,my_pad))
	print(p)
	
	
	
	### Graph plot
	clusters = df_cluster_cut$clusters
	edges = assemble_edges(clusters,need_to_debug=0)
	# edges
	p  <-  DefaultPlot()+
		geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude,
											  color = factor(clusters)), size = 2)+
		labs(title = paste("Cluster map - time",time))+
		guides(color = guide_legend(title = "Clusters"))
	
	q = p + geom_segment(aes(x = x, y = y, xend = xend, yend = yend,
						 color = cluster),
					 linewidth=1.2,
					 data = edges)
	# print(p)
	print(q)
	
	clusters_tm1 = clusters
	
} # end for time
```

# curve_ppmx
## on the package example
```{r}
# Example with balanced data.
# generate data for two clusters with 10 subjects each.

nobs <- 100
nsubject <- 2*10

set.seed(101)
xx <- seq(0,2*pi, length=nobs)
y <- cbind(replicate(n=10, 3*sin(xx)*as.numeric(xx<=pi) + rnorm(nobs,0,0.5)),
           replicate(n=10, 3*cos(xx)*as.numeric(xx<=pi) + rnorm(nobs,0,0.5)))

dat <- data.frame(y=c(y),
                  z=rep(1:nobs, times=nsubject),
                  Name=rep(1:nsubject, each=nobs))

subject_obs_vec <- dat$Name

nknots <- 15



# Small number of iterates for illustrative purposes only
niter <- 5000
nburn <- 2000
nthin <- 3
nout <- (niter-nburn)/nthin

z <- dat$z

## the order here is c(mu0, s20, v, k0, nu0, a0, alpha)
## If simularity is N-NIG then k0 and nu0 are used but v is not
## If simularity is N-N then v is used but no k0 and nu0
simparms <- c(0.0, 1.0, 0.1, 1.0, 1.0, 0.1, 1)

fits <- list()

# fit vgrf only
y <- dat$y

modelPriors <- c(0.5,      # Asig
                 1000^2,   # s2_mu
                 0,        # mb0
                 1000^2,   # s2b0
                 1,        # as2b0
                 1,        # bs2b0
                 1,        # at
                 1.0/0.05) # bt
dat


for(subj in 1:20){
	if(subj==1){
		plot(1:100,dat[which(dat$Name==subj),"y"],type="l",col="red",ylim=c(-4,4))
	} else {
		lines(dat[which(dat$Name==subj),"y"],type="l",col="red")
	}
}
for(i in 11:20){
	lines(dat[which(dat$Name==i),"y"],type="l",col="blue")
}
```

```{r}
fit <- curve_ppmx(y=cbind(y), z=z,
             subject=subject_obs_vec,
             Xcon = NULL, Xcat = NULL,
             Xconp=NULL, Xcatp=NULL,
             PPM=TRUE, M=1,
             q=3, rw_order=1, balanced=1,
             nknots=nknots,  npredobs=1,
             Aparm=100,
             modelPriors=modelPriors,
             similarity_function=1,
             consim=1, calibrate=0,
             simParms=simparms,
             mh=c(0.1, 1e-4),
             draws=niter,
             burn=nburn,
             thin=nthin)


Hmat <- fit$Hmat

# For a point estimate of partition, take first MCMC interate
# This is done only for illustrative purposes.  Recommend using
# the salso R package.

p.est <- fit$Si[1,]

nc <- length(unique(p.est))


oldpar <- par(no.readonly = TRUE)


# Plot individual subject fits.

tmp <- c(1,6,11,16)
par(mfrow=c(2,2))
for(j in tmp){
  bmn <- apply(fit$beta[j,,],1,mean)
  b0mn <- mean(fit$beta0[,j])

  ytmp <- y[dat$Name==j]

  b0vec <- rep(b0mn, nobs)

  plot(1:nobs,c(ytmp),
		  type='n',ylab="Response",
		  xlab="Time")

  points(1:nobs,ytmp)
  lines(1:nobs,  b0vec+Hmat%*%bmn, col=p.est[j],lwd=2)

}

# plot all curves in one plot
par(mfrow=c(1,1))

plot(dat$z, dat$y, type="n",ylab="",xlab="Time")

for(j in 1:nsubject){

  bmn <- apply(fit$beta[j,,],1,mean)
  b0mn <- mean(fit$beta0[,j])

  b0vec <- rep(b0mn, nobs)

  lines((1:nobs),  b0vec+Hmat%*%bmn, col=p.est[j],lwd=0.5)

}


par(oldpar)
```

It says "number of clusters = 2", so i guess that the time parameter is there ok, but the fit does not account for the possibility of changing clusters with time.

For example the data was built in such a way that there are 2 clusters at the beginning, but then they merge into a sigle one. While the fit cant account for that.


## loop fit
Ie now on our data.
```{r}
nknots <- 15 
niter <- 5000
nburn <- 2000
nthin <- 3 # we consider every nthin iteartions 
nout <- (niter-nburn)/nthin # the number of interatio that we coniser from the mcmc
simparms <- c(0.0, 1.0, 0.1, 1.0, 1.0, 0.1, 1) # WHAT IS THEIR MEANING IF WE DON'T USE COV
modelPriors <- c(0.5, # Asig
                 1000^2, # s2_mu
                 0, # mb0
                 1000^2, # s2b0
                 1, # as2b0
                 1, # bs2b0
                 1, # at
                 1.0/0.05) # bt

clusters_tm1 = NULL

for (time in 1:4){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y = df_time$AQ_pm10
	z = rep(time,105)
	subject = unique(df_weekly$IDStations)

	fit <- curve_ppmx(y=cbind(y), z, subject,
                  Xcon = NULL, Xcat = NULL,
                  Xconp=NULL, Xcatp=NULL,
                  PPM=TRUE, M=1,
                  q=3, rw_order=1, balanced=1,
                  nknots=nknots, npredobs=1,
                  Aparm=100,
                  modelPriors=modelPriors,
                  similarity_function=1,
                  consim=1, calibrate=0,
                  simParms=simparms,
                  mh=c(0.1, 1e-4),
                  draws=niter,
                  burn=nburn,
                  thin=nthin)
	
	clusters = salso(fit$Si,loss="binder")
	clusters = clusters[1:105]
	### Mode correct clusters
	clusters = mode_correct_clusters(clusters_tm1,clusters)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	
	
	### Hist plot
	df_hist = data.frame(clust_vals=clusters[1:105],ycurrent=y)
	my_pad = 2
	n_clusters = max(clusters)
	p = ggplot(df_hist, aes(ycurrent, fill = factor(clust_vals)))+
		scale_fill_manual(values = colora(n_clusters,77,0),name="Cluster")+
		geom_density(alpha = 0.3)+
		ggtitle(paste("Time",time))+
		theme_classic()+
		xlim(extrema(y)+c(-my_pad,my_pad))
	print(p)
	
	
	
	### Graph plot
	clusters = df_cluster_cut$clusters
	edges = assemble_edges(clusters,need_to_debug=0)
	# edges
	p  <-  DefaultPlot()+
		geom_point(data = df_cluster_cut, aes(x = Longitude, y = Latitude,
											  color = factor(clusters)), size = 2)+
		labs(title = paste("Cluster map - time",time))+
		guides(color = guide_legend(title = "Clusters"))
	
	q = p + geom_segment(aes(x = x, y = y, xend = xend, yend = yend,
						 color = cluster),
					 linewidth=1.2,
					 data = edges)
	# print(p)
	print(q)
	
	clusters_tm1 = clusters
	
} # end for time
```

