---
title: "ppmSuite: sppm method - model selection - data 2017"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(ppmSuite)
library(tidyverse)
library(salso)
library(zoo)
```


```{r}
source("include.R")
# source("plot functions/plotter.R")
# source("include_clusters_functions.R")
```


```{r}
# df = df_weekly %>% 
# 	select(IDStations, Latitude, Longitude, AQ_pm10, week) %>%
# 	spread(week, AQ_pm10)

df_2017 = df_agri %>% select(IDStations, Latitude, Longitude, Time, AQ_pm10) %>% 
	filter(Time >= "2017-01-01" & Time < "2018-01-01") %>%
	filter(!IDStations %in% c("STA-CH0011A","STA-CH0033A","STA-CH0043A")) %>% #problematic_stations (for year 2018)
	mutate(week = week(Time)) %>% 
	group_by(IDStations) %>% filter(sum(is.na(AQ_pm10)) <= 30) %>% #keeping stations that have less than 30 null values
	ungroup %>% mutate(AQ_pm10 = na.approx(AQ_pm10)) %>% #interpolating null values
	
	#computing the mean for each week
	group_by(IDStations, week) %>%
	summarize(IDStations = first(IDStations),
			  Latitude = first(Latitude),  Longitude = first(Longitude),
			  AQ_pm10 = mean(AQ_pm10, na.rm = TRUE), week = first(week)) %>% ungroup() %>%
	
	mutate(AQ_pm10 = log(AQ_pm10))# log-transformation



df = df_2017 %>%
	spread(week, AQ_pm10)

# glimpse(df)
head(df)
```

```{r}
# splitting train and test data
set.seed(123)
train_ind <- sample(seq_len(nrow(df)), size = 70)

df_train <- df[train_ind, ]
df_test <- df[-train_ind, ]
```


```{r}
s_coords <- data.matrix(df[,2:3]) #lat and long
# m <- dim(s_coords)[1]

# standardize spatial coordinates
smn <- apply(s_coords,2,mean)
ssd <- apply(s_coords,2,sd)
s_std <- t((t(s_coords) - smn)/ssd)


# splitting train and test data
s_std_train = s_std[train_ind,]
s_std_test <- s_std[-train_ind,] # standardized prediction spatial coordinates

```


```{r}
# MCMC parameters'
niter <- 20000
nburn <- 10000
nthin <- 10
nout <- (niter - nburn)/nthin



# sppm hyperparameters
M_list = c(1.0, 0.1, 0.01)

alpha_C1_list = c(1,2)
alpha_C2 = median(dist(s_std))# setting alpha of C2 as the median of the distances between locations


params_model = c(0, 100^2, 10, 10)# as in the paper 
# obs: in the paper observations are standardaized, but here AQ_pm10 has mean near 3.3 and the std near .4
#		so not a big problem (I think)
```


# Fitting
## M1
```{r}

M = M_list[1]
```


### C1 - 1
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[1], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M1_C1_1.RData")
```





### C1 - 2
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[2], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M1_C1_2.RData")
```


### C2
```{r}
cohesion_number = 2
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M1_C2.RData")
```

### C3
```{r}
cohesion_number = 3
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M1_C3.RData")
```

### C4
```{r}
cohesion_number = 4
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M1_C4.RData")
```


## M01
```{r}

M = M_list[2]
```


### C1 - 1
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[1], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M01_C1_1.RData")
```





### C1 - 2
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[2], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M01_C1_2.RData")
```


### C2
```{r}
cohesion_number = 2
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M01_C2.RData")
```

### C3
```{r}
cohesion_number = 3
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M01_C3.RData")
```

### C4
```{r}
cohesion_number = 4
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M01_C4.RData")
```



## M001
```{r}

M = M_list[3]
```


### C1 - 1
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[1], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M001_C1_1.RData")
```





### C1 - 2
```{r}
cohesion_number = 1
params_cohesion = c(alpha_C1_list[2], 1.5, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M001_C1_2.RData")
```


### C2
```{r}
cohesion_number = 2
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M001_C2.RData")
```

### C3
```{r}
cohesion_number = 3
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M001_C3.RData")
```

### C4
```{r}
cohesion_number = 4
params_cohesion = c(1, alpha_C2, 0, 1, 2, 1)


sppm_list = list()
for (week in 1:53){#max weeks 53
	Y <- df_train %>% pull(as.character(week))
	out <- sppm(y = Y, s = s_std_train,
				s.pred = s_std_test,
				cohesion=cohesion_number,
				M=M, 
				modelPriors = params_model,
				cParms = params_cohesion,
				mh = c(0.5, 0.5),
				draws=niter, burn=nburn, thin=nthin)
	
	
	sppm_list <- c(sppm_list, list(out))
}



save(sppm_list,file="M001_C4.RData")
```

# Comparison
```{r}
models_names = c("M1_C1_1", "M1_C1_2","M1_C2","M1_C3","M1_C4",
				 "M01_C1_1", "M01_C1_2","M01_C2","M01_C3","M01_C4",
				 "M001_C1_1", "M001_C1_2","M001_C2","M001_C3","M001_C4"
				 )
```


## Computing statistics
```{r}
stats_sppm = data.frame()

for (m_name in models_names){
	# Loading model
	load(paste(m_name, ".RData", sep = ""))
	
	# Computing statistics
	## MSE
	Y_train = as.matrix(df_train[,4:56])
	Y_fitted = matrix(0, nrow = nrow(Y_train), ncol = ncol(Y_train))
	for (w in 1:ncol(Y_pred)){
		Y_fitted[,w] = colMeans(sppm_list[[w]]$fitted)
	}
	MSE = apply(Y_train - Y_fitted, 2, FUN=function(x) mean(x^2))
	
	## MSPE
	Y_test = as.matrix(df_test[,4:56])
	Y_pred = matrix(0, nrow = nrow(Y_test), ncol = ncol(Y_test))
	for (w in 1:ncol(Y_pred)){
		Y_pred[,w] = colMeans(sppm_list[[w]]$ppred)
	}
	MSPE = apply(Y_test - Y_pred, 2, FUN=function(x) mean(x^2))
	
	## LPML and WAIC
	LPML = numeric(53)
	WAIC = numeric(53)
	for (w in 1:53){
		LPML[w] = sppm_list[[w]]$lpml
		WAIC[w] = sppm_list[[w]]$WAIC
	}
	
	
	#Binding statistics
	stats_sppm = rbind(stats_sppm,
					   data.frame(
					   	model = m_name,
					   	week = seq(53),
					   	MSE = MSE,
					   	MSPE = MSPE,
					   	LPML = LPML,
					   	WAIC = WAIC)
					   )
}

```


# Analisys

## All
```{r}
stats_sppm %>% ggplot(aes(x = model, y = MSE, colour = model)) + geom_boxplot() + 
	scale_x_discrete(guide = guide_axis(angle = 60))+ theme(legend.position = "none")
stats_sppm %>% ggplot(aes(x = model, y = MSPE, colour = model)) + geom_boxplot() + 
	scale_x_discrete(guide = guide_axis(angle = 60))+ theme(legend.position = "none")
stats_sppm %>% ggplot(aes(x = model, y = LPML, colour = model)) + geom_boxplot() + 
	scale_x_discrete(guide = guide_axis(angle = 60))+ theme(legend.position = "none")
stats_sppm %>% ggplot(aes(x = model, y = WAIC, colour = model)) + geom_boxplot() + 
	scale_x_discrete(guide = guide_axis(angle = 60))+ theme(legend.position = "none")

```

```{r}
# stats_sppm %>% group_by(model) %>% 
# 	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC))

stats_sppm %>% group_by(model) %>% 
	summarise(MSE = median(MSE)) %>%
	arrange(MSE)

stats_sppm %>% group_by(model) %>% 
	summarise(MSPE = median(MSPE)) %>%
	arrange(MSPE)

stats_sppm %>% group_by(model) %>% 
	summarise(LPML = median(LPML)) %>%
	arrange(desc(LPML))

stats_sppm %>% group_by(model) %>% 
	summarise(WAIC = median(WAIC)) %>%
	arrange(WAIC)

```

Since variability is more ore less similar and there are "outliers", we just look at the median
```{r}
# stats_sppm %>% group_by(model) %>% 
# 	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC))

stats_sppm %>% group_by(model) %>%
	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC)) %>%
	filter(str_detect(model,"C1"))

stats_sppm %>% group_by(model) %>%
	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC)) %>%
	filter(str_detect(model,"C2"))

stats_sppm %>% group_by(model) %>%
	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC)) %>%
	filter(str_detect(model,"C3"))

stats_sppm %>% group_by(model) %>%
	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC)) %>%
	filter(str_detect(model,"C4"))

```
We note that:
- for cohesion C1, for both values of alpha, the lower M the better (in terms of MSPE LPML and WAIC)
	for both M = 0.01 is better, 
		however alpha2 is better in terms of MSPE and LPML
		but alpha1 is better in terms of WAIC
					
- for cohesion C2, the lower the M the better it is (in terms of MSPE and LPML) 
	in terms of WAIC M=0.1 performs better
	in terms of LPML and MSPE M=0.01 is better

- for cohesion C3, the higher M the better it is (in terms of MSPE LPML and WAIC)
	we also note that for low M it tends to overfit
	the best is M = 1

- for cohesion C4, it works well for M = 0.1 and M = 1; 
	we also note that for low M it tends to overfit
	in terms of MSPE, both M = 0.1 and M = 1 are similar
	However in general M = 0.1 is better



## The good ones
For now on, we analyse just the good ones for each cohesion function

```{r}
good_models = c("M001_C1_1", "M001_C1_2",
				"M01_C2", "M001_C2",
				"M1_C3",
				"M01_C4")

stats_sppm  %>% filter(model %in% good_models)  %>% group_by(model) %>% 
	summarise(MSE = median(MSE), MSPE = median(MSPE), LPML = median(LPML), WAIC = median(WAIC))
```


```{r}
stats_sppm %>% filter(model %in% good_models) %>% 
	ggplot(aes(x = week, y = MSE, group = model, colour = model)) + geom_line()
stats_sppm %>% filter(model %in% good_models) %>% 
	ggplot(aes(x = week, y = MSPE, group = model, colour = model)) + geom_line()
stats_sppm %>% filter(model %in% good_models) %>% 
	ggplot(aes(x = week, y = LPML, group = model, colour = model)) + geom_line()
stats_sppm %>% filter(model %in% good_models) %>% 
	ggplot(aes(x = week, y = WAIC, group = model, colour = model)) + geom_line()

```
- In terms of MSPE the behave similarly
- we observe an eccentric behaviour of cohesion C2 in LPML in LPML


At the end, in terms of MSPE, LPML, WAIC, the best one is the cohesion function C4 with M = 0.1