---
title: "Untitled"
output: html_document
---


```{r,warning=FALSE}
source("include.R") # why didnt you use it above, in your code? :'/
source("plot functions/plotter.R")
```

If we include this alone seems to work better (dont know why).
```{r}
source("include_clusters_functions.R")
```

# cluster plots stuff
Stuff needed for the plot functions to work
```{r}
cols = colora(10,"div")[-2] # divergent palette; togliamo il giallino

y=data.frame()

for(st in stations){
  y_we_pm10=cbind(as.data.frame(st),t(df_weekly[which(df_weekly$IDStations==st),"AQ_pm10"]))
  y=rbind(y,y_we_pm10)
}

rownames(y) = NULL
colnames(y)<- c("id",paste0("w", 1:53))
df_weekly
y
# this y needs to not be overwritten
```


```{r}
library(salso)
library(ppmSuite)
```

Sometimes it fails the execution (dont know why). In that case:
- go to the file include_clusters_function.R and run it all (ctrl+alt+R)
- come back here and now it should run finely

# gaussian_ppmx

## loop fit
```{r}
clusters_old = NULL

for (time in 1:6){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y_fit = df_time$AQ_pm10
	X = df_time[,-c(1:5,7)]

	fit = gaussian_ppmx(y_fit, X=X, Xpred=NULL,
	                  meanModel=1,
	                  cohesion=1,
	                  M=1,
	                  PPM = FALSE,
	                  similarity_function=1,
	                  consim=1,
	                  calibrate=0,
	                  simParms=c(0.0, 1.0, 0.1, 1.0, 2.0, 0.1, 1),
	                  modelPriors=c(0, 100^2, 1, 1),
	                  mh=c(0.5, 0.5),
	                  draws=1100,burn=100,thin=1,
	                  verbose=FALSE)
	
	clusters_now = salso(fit$Si,loss="binder")
	clusters_now = clusters_now[1:105]
	### Mode correct clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters_now[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	
	### Hist plot
	# p = get_hist_color_plot(df_cluster_cut)
	p = get_hist_fill_plot(df_cluster_cut) # choose one of these two
	print(p)
	
	### Graph plot
	q = get_graph_plot(df_cluster_cut)
	print(q)
	
	# or both together with
	# plot_graph_and_hist(df_cluster_cut)
	
	clusters_old = clusters_now
} # end for time

cat(fit$lpml)
cat(fit$WAIC)
```
# Model sppm

## loop fit
```{r}
clusters_old = NULL

for (time in 1:5){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y_fit = df_time$AQ_pm10
	s = data.frame(
		lat = unique(df_weekly$Latitude),
		long = unique(df_weekly$Longitude)
	)

	fit = sppm(y_fit,s,
	    s.pred=NULL,
	    cohesion=3,
	    M=1,
	    modelPriors=c(0, 100^2, 10, 10),
	    cParms=c(1, 1.5, 0, 1, 2, 2),
	    mh=c(0.5, 0.5),
	    draws=1100,burn=100,thin=1)
	
	clusters_now = salso(fit$Si,loss="binder")
	clusters_now = clusters_now[1:105]
	### Mode correct clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters_now[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	
	### Hist plot
	# p = get_hist_color_plot(df_cluster_cut)
	# p = get_hist_fill_plot(df_cluster_cut) # choose one of these two
	# print(p)
	
	### Graph plot
	# q = get_graph_plot(df_cluster_cut)
	# print(q)
	
	# or both together with
	plot_graph_and_hist(df_cluster_cut)
	
	clusters_old = clusters_now
} # end for time
```

# curve_ppmx

## time management considerations
```{r}
# Example with balanced data.
# generate data for two clusters with 10 subjects each.

nobs <- 10
nsubject <- 2*10

set.seed(101)
xx <- seq(0,2*pi, length=nobs)
y_fit <- cbind(replicate(n=10, 3*sin(xx)*as.numeric(xx<=pi) + rnorm(nobs,0,0.4)),
			   replicate(n=10, 3*cos(xx)*as.numeric(xx<=pi) + rnorm(nobs,0,0.4)))

# lenght(y_fit)
dat <- data.frame(y_fit=c(y_fit),
                  z=rep(1:nobs, times=nsubject),
                  Name=rep(1:nsubject, each=nobs))

subject_obs_vec <- dat$Name

nknots <- 15

# Small number of iterates for illustrative purposes only
niter <- 5000
nburn <- 2000
nthin <- 3
nout <- (niter-nburn)/nthin

z <- dat$z

## the order here is c(mu0, s20, v, k0, nu0, a0, alpha)
## If simularity is N-NIG then k0 and nu0 are used but v is not
## If simularity is N-N then v is used but no k0 and nu0
simparms <- c(0.0, 1.0, 0.1, 1.0, 1.0, 0.1, 1)

fits <- list()

# fit vgrf only
y_fit <- dat$y_fit

modelPriors <- c(0.5,      # Asig
                 1000^2,   # s2_mu
                 0,        # mb0
                 1000^2,   # s2b0
                 1,        # as2b0
                 1,        # bs2b0
                 1,        # at
                 1.0/0.05) # bt
dat


for(subj in 1:nsubject){
	if(subj==1){
		plot(1:nobs,dat[which(dat$Name==subj),"y_fit"],type="l",col="red",ylim=c(-4,4))
	} else {
		lines(dat[which(dat$Name==subj),"y_fit"],type="l",col="red")
	}
}
for(i in 11:20){
	lines(dat[which(dat$Name==i),"y_fit"],type="l",col="blue")
}
```

Caso problematico in cui ci sono due cluster all'inizio ma ad un certo punto il modello dovrebbe darne solo uno, quando si riuniscono.

Gaussian ppmx non sembra accorgersi, dà anche molti cluster.
```{r}
fit = gaussian_ppmx(y_fit, X=NULL, Xpred=NULL,
                  meanModel=1,
                  cohesion=1,
                  M=1,
                  PPM = FALSE,
                  similarity_function=1,
                  consim=1,
                  calibrate=0,
                  simParms=c(0.0, 1.0, 0.1, 1.0, 2.0, 0.1, 1),
                  modelPriors=c(0, 100^2, 1, 1),
                  mh=c(0.5, 0.5),
                  draws=1100,burn=100,thin=1,
                  verbose=FALSE)
clusters_now = salso(fit$Si,loss="binder",maxNClusters = 8)
clusters_now

cols = colora(12,"div")[-c(2)]
for(subj in 1:nsubject){
	if(subj==1){
		plot(1:nobs,dat[which(dat$Name==subj),"y_fit"],type="l",col=cols[clusters_now[subj]],ylim=c(-4,4))
	} else {
		lines(dat[which(dat$Name==subj),"y_fit"],type="l",col=cols[clusters_now[subj]])
	}
}
```



Curve ppmx dà due cluster ma perché in effetti ce ne sono due all'inizio, ma non notifica quando si reincontrano.
```{r}
fit <- curve_ppmx(y=cbind(y_fit), z=z,
             subject=subject_obs_vec,
             Xcon = NULL, Xcat = NULL,
             Xconp=NULL, Xcatp=NULL,
             PPM=TRUE, M=1,
             q=3, rw_order=1, balanced=1,
             nknots=nknots,  npredobs=1,
             Aparm=100,
             modelPriors=modelPriors,
             similarity_function=1,
             consim=1, calibrate=0,
             simParms=simparms,
             mh=c(0.1, 1e-4),
             draws=niter,
             burn=nburn,
             thin=nthin)

clusters_now = salso(fit$Si,loss="binder",maxNClusters = 8)
clusters_now

Hmat <- fit$Hmat

# For a point estimate of partition, take first MCMC interate
# This is done only for illustrative purposes.  Recommend using
# the salso R package.

p.est <- fit$Si[1,]

nc <- length(unique(p.est))

oldpar <- par(no.readonly = TRUE)

# Plot individual subject fits.

tmp <- c(1,6,11,16)
par(mfrow=c(2,2))
for(j in tmp){
  bmn <- apply(fit$beta[j,,],1,mean)
  b0mn <- mean(fit$beta0[,j])

  ytmp <- y_fit[dat$Name==j]

  b0vec <- rep(b0mn, nobs)

  plot(1:nobs,c(ytmp),
		  type='n',ylab="Response",
		  xlab="Time")

  points(1:nobs,ytmp)
  lines(1:nobs,  b0vec+Hmat%*%bmn, col=p.est[j],lwd=2)

}

# plot all curves in one plot
par(mfrow=c(1,1))

plot(dat$z, dat$y_fit, type="n",ylab="",xlab="Time")

for(j in 1:nsubject){

  bmn <- apply(fit$beta[j,,],1,mean)
  b0mn <- mean(fit$beta0[,j])

  b0vec <- rep(b0mn, nobs)

  lines((1:nobs),  b0vec+Hmat%*%bmn, col=p.est[j],lwd=0.5)

}


par(oldpar)
```

It says "number of clusters = 2", so i guess that the time parameter is there ok, but the fit does not account for the possibility of changing clusters with time.

For example the data was built in such a way that there are 2 clusters at the beginning, but then they merge into a sigle one. While the fit cant account for that.


## loop fit
Ie now on our data.
```{r}
nknots <- 15 
niter <- 5000
nburn <- 2000
nthin <- 3 # we consider every nthin iteartions 
nout <- (niter-nburn)/nthin # the number of interatio that we coniser from the mcmc
simparms <- c(0.0, 1.0, 0.1, 1.0, 1.0, 0.1, 1) # WHAT IS THEIR MEANING IF WE DON'T USE COV
modelPriors <- c(0.5, # Asig
                 1000^2, # s2_mu
                 0, # mb0
                 1000^2, # s2b0
                 1, # as2b0
                 1, # bs2b0
                 1, # at
                 1.0/0.05) # bt

clusters_old = NULL

for (time in 1:4){
	cat(crayon::red("Time (ie week)",time,"\n"))
	df_time = df_weekly[which(df_weekly$week==time),]
	y_fit = df_time$AQ_pm10
	z = rep(time,105)
	subject = unique(df_weekly$IDStations)

	fit <- curve_ppmx(y=cbind(y_fit), z, subject,
                  Xcon = NULL, Xcat = NULL,
                  Xconp=NULL, Xcatp=NULL,
                  PPM=TRUE, M=1,
                  q=3, rw_order=1, balanced=1,
                  nknots=nknots, npredobs=1,
                  Aparm=100,
                  modelPriors=modelPriors,
                  similarity_function=1,
                  consim=1, calibrate=0,
                  simParms=simparms,
                  mh=c(0.1, 1e-4),
                  draws=niter,
                  burn=nburn,
                  thin=nthin)
	
	clusters_now = salso(fit$Si,loss="binder")
	clusters_now = clusters_now[1:105]
	### Mode correct clusters
	clusters_now = mode_correct_clusters(clusters_old,clusters_now)
	
	df_temp = data.frame(
		Longitude = unique(df_weekly$Longitude),
		Latitude = unique(df_weekly$Latitude),
		clusters = clusters_now[1:105]
	)
	df_temp$Time = rep(time,dim(df_temp)[1])
	df_cluster_cut = df_temp
	
	### Hist plot
	# p = get_hist_color_plot(df_cluster_cut)
	# p = get_hist_fill_plot(df_cluster_cut) # choose one of these two
	# print(p)
	
	### Graph plot
	# q = get_graph_plot(df_cluster_cut)
	# print(q)
	
	# or both together with
	plot_graph_and_hist(df_cluster_cut)
	
	clusters_old = clusters_now
} # end for time
```

