---
title: "R Notebook"
output: html_document
---

install.packages("ppmSuite")
```{r}
library(ppmSuite)
```

# Test ppmSuite
```{r}
head(ppmSuite::bear)
# it's a dataset of ppmSuite
# If there is output it means that it works, the package is correctly installed
```




# Test drpm
https://www.tandfonline.com/doi/suppl/10.1080/10618600.2021.1987255?scroll=top
devtools::install_github("https://github.com/gpage2990/drpm.git")
```{r}
library(drpm)
library(salso)
```
```{r}
# preparation
source("include.R") # for having df_agri

sites = data.frame(
	longitude = unique(df_agri$Longitude)[1:10], 
	latitude = unique(df_agri$Latitude)[1:10])

# unique(df_agri[,c("Longitude","Latitude")])[1:10,] == sites[1:10,]
```


# Step 1
## on simulated data
```{r}
# begin all in the same cluster
y01=matrix(data=rnorm(5,0,1),nrow = 5,ncol = 1)
y02=matrix(data=rnorm(5,0,1),nrow = 5,ncol = 1)
y0 = rbind(y01,y02)

# half in cluster 0, half in cluster 1
y11=matrix(data=rnorm(5,0,1),nrow = 5,ncol = 1)
# cambiato da 10 a 50 così i cluster sono più separati
y12=matrix(data=rnorm(5,50,1),nrow = 5,ncol = 1)
y1 = rbind(y11,y12)

# at time 2 they switch clusters
y21=matrix(data=rnorm(5,50,1),nrow = 5,ncol = 1)
y22=matrix(data=rnorm(5,0,1),nrow = 5,ncol = 1)
y2 = rbind(y21,y22)

# at time 3 they move in a new cluster
y31=matrix(data=rnorm(5,100,1),nrow = 5,ncol = 1)
y32=matrix(data=rnorm(5,100,1),nrow = 5,ncol = 1)
y3 = rbind(y31,y32)

# at time 4 they return to the clusters at 1
y41=matrix(data=rnorm(5,0,1),nrow = 5,ncol = 1)
y42=matrix(data=rnorm(5,50,1),nrow = 5,ncol = 1)
y4 = rbind(y41,y42)

y = cbind(y0,y1,y2,y3,y4)
as.data.frame(y)


cols = colora(size(y)[1],56,0)
for(i in 1:size(y)[1]){
	if(i==1){
		plot(y[i,],col=cols[i],ylim=extrema(y),type="l")
	}
	else{
		lines(y[i,],col=cols[i])
	}
}
abline(h=c(0,50,100),col=cols[1])
text(4,0,"CL1")
text(4,50,"CL2")
text(4,100,"CL3")
```
```{r}
fit_sim <- drpm_fit(y,
		s_coords = NULL, # per ora cerchiamo solo di capire i cluster, senza spatial effect
		M=1,
		initial_partition = NULL,
		starting_alpha = 0.5,
		unit_specific_alpha = FALSE,
		time_specific_alpha = TRUE,
		alpha_0=FALSE,
		eta1_0=FALSE,
		phi1_0=FALSE,
		modelPriors=c(40,100^2,1,1,1,1),
		alphaPriors=rbind(c(1,1)),
		simpleModel = 0,
		theta_tau2 = c(0, 2),
		SpatialCohesion=4,
		cParms=c(0, 1, 2, 1),
		mh=c(0.5, 1, 0.1, 0.1, 0.1),
		verbose=TRUE,
		draws=1100,burn=100,thin=1)
```

## understand salso
```{r}
names(fit_sim)
size(fit_sim$Si)
# ?salso
```

Salso wants
- as x a B*n matrix, where B stands for the MCMC iterates, and the n cols stands for the cluster assigned to the units (in that MCMC iterate).
So there is no time account here, in salso (while there was in the model). So maybe we just have to extract the best partition at each time. Le partizioni di salso non dipendono dal tempo, ma quelle generate da drpm_fit sì, quindi non è che il tempo "scompare", resta presente nell'input che diamo a salso.

For example here we get, for time instant 1, the 1000 simulated values for the clustering of our 10 units.
Indeed they all started at the same level so makes sense they are in cluster 1 all.

```{r}
cat("Requested size by salso: ")
size(t(fit_sim$Si[1,,]))

for(time in 1:5){
	cat("\nTime",time,"\n")
	if(time==1) cat("all the same cluster\n")
	if(time==2) cat("two clusters separated\n")
	if(time==3) cat("again two clusters separated, but the cluster index does not change, as indeed the observations dont mix, they follow different paths.\nCioè quelle che prima erano alte ora scendono, ma non per questo il loro cluster number deve cambiare.\nPrima erano cluster 2 e ora rimangano cluster 2 anche sono \"in basso\".\n")
	if(time==4) cat("all the same cluster\n")
	if(time==5) cat("again two clusters\n")
	
print(t(fit_sim$Si[time,,])[1:10,])
}
```

## get final best partitions
```{r}
cat("We had units from 1 to 10.\n")
for (time in 1:5){
	cat("\nBest partition at time",time,"is\n")
	salso_out = suppressWarnings({
		salso( x =t(fit_sim$Si[time,,]), loss = "binder")
	})
	cat(salso_out)
}
```


Steps to follow maybe, just ideas

# Step 1.5
## on simulated mixing data
as the example of step 1 but with interlacing data, like this:
```{r}
sigma2 = 0.2
y0 = c(0,0,0,0)+rnorm(4,0,sigma2)   # all same cluster 
y1 = c(4,-2,-2,4)+rnorm(4,0,sigma2) # cluster 1&4, 2&3
y2 = c(4,4,-2,-2)+rnorm(4,0,sigma2) # cluster 1&2, 3&4
y3 = c(-2,6,6,6)+rnorm(4,0,sigma2)  # cluster 1, 2&3&4

y = cbind(y0,y1,y2,y3)

cols = colora(size(y)[1],56,0)
for(i in 1:size(y)[1]){
	if(i==1){
		plot(y[i,],col=cols[i],ylim=extrema(y),type="l")
	}
	else{
		lines(y[i,],col=cols[i])
	}
}
legend("topleft",c("obs1","obs2","obs3","obs4"),fill=cols)
```


```{r}
# 1 point 5, the step
fit_sim_1p5 <- drpm_fit(y,
		s_coords = NULL, # per ora cerchiamo solo di capire i cluster, senza spatial effect
		M=1,
		initial_partition = NULL,
		starting_alpha = 0.5,
		unit_specific_alpha = FALSE,
		time_specific_alpha = TRUE,
		alpha_0=FALSE,
		eta1_0=FALSE,
		phi1_0=FALSE,
		modelPriors=c(40,100^2,1,1,1,1),
		alphaPriors=rbind(c(1,1)),
		simpleModel = 0,
		theta_tau2 = c(0, 2),
		SpatialCohesion=4,
		cParms=c(0, 1, 2, 1),
		mh=c(0.5, 1, 0.1, 0.1, 0.1),
		verbose=TRUE,
		draws=1100,burn=100,thin=1)
```

```{r}
cat("We had units from 1 to 4.\n")
for (time in 1:size(y)[1]){
	cat("\nBest partition at time",time,"is\n")
	salso_out = suppressWarnings({
		salso( x =t(fit_sim_1p5$Si[time,,]), loss = "binder")
	})
	cat(salso_out)
	if(time == 1) cat(" (all same cluster)")
	if(time == 2) cat(" (cluster 1&4, 2&3)")
	if(time == 3) cat(" (cluster 1&2, 3&4)")
	if(time == 4) cat(" (cluster 1, 2&3&4)")
}
```


```{r}
summary(salso_out)
```




# Step 2
## on simulated spatial data
o forse no passiamo direttamente allo step 3.












```{r}
names(drpm1)
```



















